---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


library(readxl)
library(tidyverse)
library(cowplot)
library(ggthemes)

```



```{r}
d <- readxl::read_excel("C:/Users/drk8b9/Desktop/phase_analysis/test_ctrl_waves.xlsx")
```

```{r}
# ggplot(d)+
#   geom_line(aes(x = Time, y = IN4), color = "steelblue")+
#   geom_line(aes(x = Time, y = IN9), color = "firebrick")+
#   geom_line(aes(x = Time, y = (2*IN14)-56), color = "steelblue")


```


```{r}
# create artificial dataset:
d <- d[, c("Time", "IN4",  "IN9", "IN14")]

d$IN9 <- c(d$IN9[13963:nrow(d)], d$IN9[1:13962])
d$IN15 <- c(d$IN14[13963:nrow(d)], d$IN14[1:13962])

d$Time <- d$Time/1000

d$Time <- d$Time - min(d$Time)
```

## dVdT
```{r}


# ggplot(d, aes(x = IN9, y = IN9.dVdT, color = Time))+
#   geom_point()
# geom_path()
# ggforce::geom_link2()



# cowplot::plot_grid(plotlist = list(
# ggplot(d)+
#   geom_line(aes(x = Time, y = IN9)),
# 
# ggplot(d)+
#   geom_point(aes(x = Time, y = IN9.dVdT), color = "red")+
#   geom_line(aes(x = Time, y = IN9.dVdT)),
# 
# ggplot(d)+
#   geom_point(aes(x = Time, y = abs(IN9.dVdT)), color = "red")+
#   geom_line(aes(x = Time, y = abs(IN9.dVdT)))
# ), ncol = 1)

```

## using abs(dVdT) and a max interval to define bursts
```{r eval=FALSE, include=FALSE}
# ggplot(d)+
#   geom_point(aes(x = Time, y = abs(IN9.dVdT)), color = "red")+
#   geom_line(aes(x = Time, y = abs(IN9.dVdT)))+
#   geom_hline(yintercept = 5)


dVdT.thresh <- 5
max.gap <- 0.5

d$IN9.dVdT.thresh <- F

d[(d$IN9.dVdT > dVdT.thresh |
    d$IN9.dVdT < (-1*dVdT.thresh)) &
    !is.na(d$IN9.dVdT), "IN9.dVdT.thresh"] <- T


# ggplot(d)+
#   geom_line(aes(x = Time, y = abs(IN9.dVdT)))+
#   geom_point(aes(x = Time, y = abs(IN9.dVdT), color = IN9.dVdT.thresh))


# finds start/end times by shifting the logical vector, up 1, down 1 and 0, then adding all three. The start/end time should have a value of 2, inside the event a value of 3

d$start.end <- 

as.numeric(d$IN9.dVdT.thresh[seq(from = 1, to = length(d$IN9.dVdT.thresh), by  = 1)]) +
  # Shift all values up by one
  c(as.numeric(d$IN9.dVdT.thresh[seq(from = 2, to = length(d$IN9.dVdT.thresh), by  = 1)]),
  0)+
  # Shift all values down by one.
  c(0,
  as.numeric(d$IN9.dVdT.thresh[seq(from = 1, to = (length(d$IN9.dVdT.thresh)-1), by  = 1)])) 
  
ggplot(d)+
  geom_line(aes(x = Time, y = abs(IN9.dVdT)))+
  geom_point(aes(x = Time, y = abs(IN9.dVdT), color = as.factor(start.end)))+
  geom_vline(xintercept = unlist(d[d$start.end == 1, "Time"]), na.rm = T)

# Check in between to see which events need to be extended based on maximum gap

## get a list of transitions
transition <- base::which(d$start.end == 2)
## reduce to evens since we're only interested in extending events, so we can ignore the start of events
#transition <- transition[seq_along(transition)%%2 == 0]


### ####
for (i in seq_along(transition)){
  print(i)
print(d[transition[i], ])

as.numeric(d[transition[i], "Time"])
# find the last value in gap which is above threshold
event.threshold.vector <- 
  d[d$Time >= as.numeric(d[transition[i], "Time"])&
    d$Time <  as.numeric(d[transition[i], "Time"])+max.gap, "IN9.dVdT.thresh"] %>% unlist()

event.time.vector <- 
  d[d$Time >= as.numeric(d[transition[i], "Time"])&
    d$Time <  as.numeric(d[transition[i], "Time"])+max.gap, "Time"] %>% unlist()

last.above.threshold <- base::which(event.threshold.vector[!is.infinite(event.threshold.vector)] == T) %>% max(., na.rm = T)

new.event.end.time <- event.time.vector[last.above.threshold]

# new event end time threshold value becomes 2 since it's now an end and everything inbetween becomes 3
d[seq((transition[i]+1),
      (transition[i] + last.above.threshold)), "start.end"] <- 3
#d[(transition[i] + last.above.threshold-1), "start.end"] <- 2


# if we haven't exceeded the next transition time run again, if we have stop
}

##
d[d$start.end >= 2, "start.end"] <- 3


ggplot(d)+
  geom_line(aes(x = Time, y = abs(IN9.dVdT)))+
  geom_point(aes(x = Time, y = abs(IN9.dVdT), color = as.factor(start.end)))+
  geom_vline(xintercept = unlist(d[d$start.end == 1, "Time"]), na.rm = T)





```

```{r}



# ggplot(df)+
#   geom_line(aes(x = Time, y = abs(IN9.dVdT)))+
#   geom_point(aes(x = Time, y = abs(IN9.dVdT), color = as.factor(assignment.vector)))
  # geom_vline(xintercept = unlist(df[df$start.end == 1, "Time"]), na.rm = T)
```

```{r}
d <- full_join(d, return_dVdT(df = d,
                        channel = "IN4",
                        time.channel = "Time",
                        time.step = 0.05,
                        dVdT.channel.name = "IN4.dVdT"))

d <- full_join(d, return_dVdT(df = d,
                        channel = "IN9",
                        time.channel = "Time",
                        time.step = 0.05,
                        dVdT.channel.name = "IN9.dVdT"))

d <- full_join(d, mk_burst(df = d,
                           # channel = "IN4",
                           time.channel = "Time",
                           dVdT.channel.name = "IN4.dVdT",
                           
                           dVdT.thresh = 5,
                           max.gap = 0.5,
                           event.channel.name = "IN4.Bursts"))

d <- full_join(d, mk_burst(df = d,
                           # channel = "IN9",
                           time.channel = "Time",
                           dVdT.channel.name = "IN9.dVdT",
                           
                           dVdT.thresh = 5,
                           max.gap = 0.5,
                           event.channel.name = "IN9.Bursts"))


```


### Reality check: Confirm annotations are working
```{r eval=FALSE, include=FALSE}

ggplot(d[,])+
  geom_line(aes(x = Time, y = IN4, color = IN4.Bursts, group = 1))+
  geom_point(data = d[d$IN4.Bursts %in% c("Start", "End"),], aes(x = Time, y = IN4, color = IN4.Bursts), size = 2)+
  geom_line(aes(x = Time, y = IN9, color = IN9.Bursts, group = 1))+
  geom_point(data = d[d$IN9.Bursts %in% c("Start", "End"),], aes(x = Time, y = IN9, color = IN9.Bursts), size = 2)+
  ggsci::scale_color_d3()
  


```


### Reality check: Correlations with pooled bursts
```{r eval=FALSE, include=FALSE}
cowplot::plot_grid(plotlist = list(

ggplot(d[,])+
  geom_path(aes(x = IN4, y = IN9, color = IN4.Bursts, group = 1))+
  geom_point(data = d[d$IN4.Bursts %in% c("Start", "End"),], aes(x = IN4, y = IN9, color = IN4.Bursts), size = 2)+
  labs(title = paste("Spearman = ", as.character(round(cor(x = d$IN4, y = d$IN9, method = c("spearman")), digits = 3))))+
  ggsci::scale_color_d3(),

ggplot(d[,])+
  geom_path(aes(x = IN4, y = IN9, color = IN9.Bursts, group = 1))+
  geom_point(data = d[d$IN9.Bursts %in% c("Start", "End"),], aes(x = IN4, y = IN9, color = IN9.Bursts), size = 2)+
  labs(title = paste("Spearman = ", as.character(round(cor(x = d$IN4, y = d$IN9, method = c("spearman")), digits = 3))))+
  ggsci::scale_color_d3(),

# IN4 bursts
ggplot(d[d$IN4.Bursts == "Event",])+
  geom_path(aes(x = IN4, y = IN9, color = IN4.Bursts, group = 1))+
  geom_point(data = d[d$IN4.Bursts %in% c("Start", "End"),], aes(x = IN4, y = IN9, color = IN4.Bursts), size = 2)+
  labs(title = paste("Spearman = ", as.character(round(cor(x = d[d$IN4.Bursts == "Event", "IN4"], y = d[d$IN4.Bursts == "Event", "IN9"], method = c("spearman")), digits = 3))))+
  ggsci::scale_color_d3(),

ggplot(d[d$IN4.Bursts == "Event",])+
  geom_path(aes(x = IN4, y = IN9, color = IN9.Bursts, group = 1))+
  geom_point(data = d[d$IN9.Bursts %in% c("Start", "End"),], aes(x = IN4, y = IN9, color = IN9.Bursts), size = 2)+
  labs(title = paste("Spearman = ", as.character(round(cor(x = d[d$IN4.Bursts == "Event", "IN4"], y = d[d$IN4.Bursts == "Event", "IN9"], method = c("spearman")), digits = 3))))+
  ggsci::scale_color_d3(),

# IN9 bursts
ggplot(d[d$IN9.Bursts == "Event",])+
  geom_path(aes(x = IN4, y = IN9, color = IN4.Bursts, group = 1))+
  geom_point(data = d[d$IN4.Bursts %in% c("Start", "End"),], aes(x = IN4, y = IN9, color = IN4.Bursts), size = 2)+
  labs(title = paste("Spearman = ", as.character(round(cor(x = d[d$IN9.Bursts == "Event", "IN4"], y = d[d$IN9.Bursts == "Event", "IN9"], method = c("spearman")), digits = 3))))+
  ggsci::scale_color_d3(),


ggplot(d[d$IN9.Bursts == "Event",])+
  geom_path(aes(x = IN4, y = IN9, color = IN9.Bursts, group = 1))+
  geom_point(data = d[d$IN9.Bursts %in% c("Start", "End"),], aes(x = IN4, y = IN9, color = IN9.Bursts), size = 2)+
  labs(title = paste("Spearman = ", as.character(round(cor(x = d[d$IN9.Bursts == "Event", "IN4"], y = d[d$IN9.Bursts == "Event", "IN9"], method = c("spearman")), digits = 3))))+
  ggsci::scale_color_d3()


), ncol = 2, labels = c("IN4", "IN9",
                        "IN4 Bursts", "",
                        "IN9 Bursts", ""))


```



### V vs dVdT plot
```{r eval=FALSE, include=FALSE}
ggplot(d[, ], aes(x = IN9, y = IN9.dVdT, color = Time))+
  geom_path()+
  geom_point()+
  ggthemes::scale_color_continuous_tableau()
  


```


## Get phase for each burst and and R^{2}
```{r}




# temp <- solve_delay_period_phase()
# hist(temp$IN9.IN4.Delay)
# hist(temp$IN9.IN4.Phase)
# hist(temp$IN9.IN4.Period)

```


```{r}
d <- full_join(d, solve_delay_period_phase(df = d,
                                           time.channel = "Time",
                                           ref.event.channel = "IN4.Bursts",
                                           contrast.event.channel = "IN9.Bursts",
                                           relevant.feature = "Start", # or "End"
                                           output.channel.prefix = "IN4.IN9"))

d <- full_join(d, solve_delay_period_phase(df = d,
                                           time.channel = "Time",
                                           ref.event.channel = "IN9.Bursts",
                                           contrast.event.channel = "IN4.Bursts",
                                           relevant.feature = "Start", # or "End"
                                           output.channel.prefix = "IN9.IN4"))
```


### Reality check: Are Delay, Period, and Phase approximately correct?
```{r eval=FALSE, include=FALSE}
cowplot::plot_grid(plotlist = list(

ggplot(d[,])+
  geom_line(aes(x = Time, y = IN4, color = IN4.IN9.Delay, group = 1))+
  geom_line(aes(x = Time, y = IN9, color = IN4.IN9.Delay, group = 1)),

ggplot(d[,])+
  geom_line(aes(x = Time, y = IN4, color = IN9.IN4.Delay, group = 1))+
  geom_line(aes(x = Time, y = IN9, color = IN9.IN4.Delay, group = 1)),


ggplot(d[,])+
  geom_line(aes(x = Time, y = IN4, color = IN4.IN9.Period, group = 1))+
  geom_line(aes(x = Time, y = IN9, color = IN4.IN9.Period, group = 1)),

ggplot(d[,])+
  geom_line(aes(x = Time, y = IN4, color = IN9.IN4.Period, group = 1))+
  geom_line(aes(x = Time, y = IN9, color = IN9.IN4.Period, group = 1)),


ggplot(d[,])+
  geom_line(aes(x = Time, y = IN4, color = IN4.IN9.Phase, group = 1))+
  geom_line(aes(x = Time, y = IN9, color = IN4.IN9.Phase, group = 1)),

ggplot(d[,])+
  geom_line(aes(x = Time, y = IN4, color = IN9.IN4.Phase, group = 1))+
  geom_line(aes(x = Time, y = IN9, color = IN9.IN4.Phase, group = 1))
  
), ncol = 2, nrow = 3)
```


## Get within burst correlation
```{r}

```


```{r}
d <- full_join(d, return_within_event_cor(df = d,
                                  time.channel = "Time",
                                  ref.channel = "IN4",
                                  contrast.channel = "IN9",
                                  event.channel = "IN4.Bursts",
                                  start.feature = "Start",
                                  event.feature = "Event",
                                  cor.channel.name = "IN4.Corr",
                                  correlation.method = "pearson" # c("pearson", "kendall", "spearman")
                                  ))

d <- full_join(d, return_within_event_cor(df = d,
                                  time.channel = "Time",
                                  ref.channel = "IN9",
                                  contrast.channel = "IN4",
                                  event.channel = "IN9.Bursts",
                                  start.feature = "Start",
                                  event.feature = "Event",
                                  cor.channel.name = "IN9.Corr",
                                  correlation.method = "pearson" # c("pearson", "kendall", "spearman")
                                  ))
```

### Reality check: Does event.feature alter output??
```{r  eval=FALSE, include=FALSE}
d <- full_join(d, return_within_event_cor(df = d,
                                  time.channel = "Time",
                                  ref.channel = "IN4",
                                  contrast.channel = "IN9",
                                  event.channel = "IN4.Bursts",
                                  start.feature = "Start",
                                  event.feature = "All",
                                  cor.channel.name = "IN4.Corr.All",
                                  correlation.method = "pearson" # c("pearson", "kendall", "spearman")
                                  ))

d <- full_join(d, return_within_event_cor(df = d,
                                  time.channel = "Time",
                                  ref.channel = "IN9",
                                  contrast.channel = "IN4",
                                  event.channel = "IN9.Bursts",
                                  start.feature = "Start",
                                  event.feature = "All",
                                  cor.channel.name = "IN9.Corr.All",
                                  correlation.method = "pearson" # c("pearson", "kendall", "spearman")
                                  ))


cowplot::plot_grid(plotlist = list(
ggplot(d, aes(x = IN4.IN9.Phase, y = IN4.Corr))+
  geom_point()+
  coord_cartesian(ylim = c(-1,1)),

ggplot(d, aes(x = IN9.IN4.Phase, y = IN9.Corr))+
  geom_point()+
  coord_cartesian(ylim = c(-1,1)),

ggplot(d, aes(x = IN4.IN9.Phase, y = IN4.Corr.All))+
  geom_point()+
  coord_cartesian(ylim = c(-1,1)),

ggplot(d, aes(x = IN9.IN4.Phase, y = IN9.Corr.All))+
  geom_point()+
  coord_cartesian(ylim = c(-1,1))
))
```


## Testing with a single experiment

```{r eval=FALSE, include=FALSE}
#install.packages("readABF")
test <- readABF::readABF(file = "S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/180117_inverted_wave/raw/180125_0075.abf")

#plot(test)

plot(x = 1:80003,
y = test$data[[1]][, 1],
type = "l")



```


```{r eval=FALSE, include=FALSE}

tic <- Sys.time()

trace <- readABF::readABF(file = "S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/190411_0034.abf")

# plot(trace)



plot(x = seq(from = trace$header$lFileStartTime, 
             to = trace$header$recTime[2], 
             length.out = 1500000),
             #by = trace$samplingIntervalInSec), 
     y = trace$data[[1]][, 1],
     type = "l")



print(Sys.time() - tic)
```


```{r}
library(readABF)



```


# Reality check: Using a known end point (voltage clamp files) can we derive the expected results?
```{r eval=FALSE, include=FALSE}


protocol_records <- c(
# 0
"S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/180507_replicate_0/raw/180509_0044.abf",

# 22.5
"S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/180207_phase_shift_reorganized/raw/181001_0012.abf",

# 45
"S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/180411_replicate_45/raw/180625_0022.abf",

# 90
"S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/190319_common_waveform_90/190408_0026.abf",

#TEA
"S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/180205_TEA_wave_in_control/raw/180223_0064.abf",

# TEA_22.5
"S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/180521_TEA_wave_22_deg/raw/180615_0029.abf",

# inverted
"S:/Data_Daniel/ActiveProjects/181015_electrical_synapses_voltage_modification/experiments/180117_inverted_wave/raw/180205_0061.abf"
)

traces <- purrr::map(protocol_records, function(i){
  load_ABF_as_matrix(path = i)
})
```


```{r eval=FALSE, include=FALSE}
# library(janitor)
dim(d)

i=2
my.plots <- purrr::map(seq_along(traces), function(i){
d <- traces[[i]] %>% as.data.frame()

names(d) <- c("IN4", "IN9", "Time")

# #Because we throw away the last burst, we must repeat the data
d <- rbind(d, d)
time.interval <- d[2, "Time"] - d[1, "Time"]
d$Time <- seq(from = 0, by = time.interval, length.out = nrow(d))


d <- full_join(d, return_dVdT(df = d,
                        channel = "IN4",
                        time.channel = "Time",
                        time.step = 0.05,
                        dVdT.channel.name = "IN4.dVdT"))

d <- full_join(d, return_dVdT(df = d,
                        channel = "IN9",
                        time.channel = "Time",
                        time.step = 0.05,
                        dVdT.channel.name = "IN9.dVdT"))

# ggplot(d[round(seq(1, to = nrow(d), length.out = 10000), digits = 0), ])+
#   geom_line(aes(x = Time, y = IN4.dVdT), color = "red")+
#   geom_line(aes(x = Time, y = IN9.dVdT), color = "blue")


d <- full_join(d, mk_burst(df = d,
                           # channel = "IN4",
                           time.channel = "Time",
                           dVdT.channel.name = "IN4.dVdT",
                           
                           dVdT.thresh = 15,
                           max.gap = 0.5,
                           event.channel.name = "IN4.Bursts"))

d <- full_join(d, mk_burst(df = d,
                           # channel = "IN9",
                           time.channel = "Time",
                           dVdT.channel.name = "IN9.dVdT",
                           
                           dVdT.thresh = 15,
                           max.gap = 0.5,
                           event.channel.name = "IN9.Bursts"))

# ggplot(d[round(seq(1, to = nrow(d), length.out = 10000), digits = 0), ])+
#   geom_point(aes(x = Time, y = IN4, color = IN4.Bursts))+
#   geom_point(aes(x = Time, y = IN9, color = IN9.Bursts))


d <- full_join(d, solve_delay_period_phase(df = d,
                                           time.channel = "Time",
                                           ref.event.channel = "IN4.Bursts",
                                           contrast.event.channel = "IN9.Bursts",
                                           relevant.feature = "Start", # or "End"
                                           output.channel.prefix = "IN4.IN9"))

d <- full_join(d, solve_delay_period_phase(df = d,
                                           time.channel = "Time",
                                           ref.event.channel = "IN9.Bursts",
                                           contrast.event.channel = "IN4.Bursts",
                                           relevant.feature = "Start", # or "End"
                                           output.channel.prefix = "IN9.IN4"))

# ggplot(d[round(seq(1, to = nrow(d), length.out = 10000), digits = 0), ])+
#   geom_path(aes(x = Time, y = IN4, color = as.factor(1/IN4.IN9.Phase)))+
#   geom_path(aes(x = Time, y = IN9, color = as.factor(1/IN9.IN4.Phase)))+
#   xlim(0, 3)


d <- full_join(d, return_within_event_cor(df = d,
                                  time.channel = "Time",
                                  ref.channel = "IN4",
                                  contrast.channel = "IN9",
                                  event.channel = "IN4.Bursts",
                                  start.feature = "Start",
                                  event.feature = "Event",
                                  cor.channel.name = "IN4.Corr",
                                  correlation.method = "pearson" # c("pearson", "kendall", "spearman")
                                  ))

d <- full_join(d, return_within_event_cor(df = d,
                                  time.channel = "Time",
                                  ref.channel = "IN9",
                                  contrast.channel = "IN4",
                                  event.channel = "IN9.Bursts",
                                  start.feature = "Start",
                                  event.feature = "Event",
                                  cor.channel.name = "IN9.Corr",
                                  correlation.method = "pearson" # c("pearson", "kendall", "spearman")
                                  ))


d <- full_join(d, return_within_event_cor(df = d,
                                  time.channel = "Time",
                                  ref.channel = "IN4",
                                  contrast.channel = "IN9",
                                  event.channel = "IN4.Bursts",
                                  start.feature = "Start",
                                  event.feature = "All",
                                  cor.channel.name = "IN4.Corr.All",
                                  correlation.method = "pearson" # c("pearson", "kendall", "spearman")
                                  ))

d <- full_join(d, return_within_event_cor(df = d,
                                  time.channel = "Time",
                                  ref.channel = "IN9",
                                  contrast.channel = "IN4",
                                  event.channel = "IN9.Bursts",
                                  start.feature = "Start",
                                  event.feature = "All",
                                  cor.channel.name = "IN9.Corr.All",
                                  correlation.method = "pearson" # c("pearson", "kendall", "spearman")
                                  ))

# "IN4"            "IN9"            "Time"           "IN4.dVdT"       "IN9.dVdT"      
# "IN4.Bursts"     "IN9.Bursts"     "IN4.IN9.Delay"  "IN4.IN9.Period" "IN4.IN9.Phase" 
# "IN9.IN4.Delay"  "IN9.IN4.Period" "IN9.IN4.Phase"  "IN4.Corr"       "IN9.Corr"    

#TODO work with 22 deg data (or another of the known phases) and get this to recapitulate the known end point
#TODO May need to redo the function that calculates phase to get it operational

plts <- cowplot::plot_grid(plotlist = list(

ggplot(d[round(seq(1, to = nrow(d), length.out = 1000), digits = 0), ])+
  geom_path(aes(x = Time, y = IN4, color = as.factor(round((1/IN4.IN9.Phase), digits = 3))))+
  geom_path(aes(x = Time, y = IN9, color = as.factor(round((1/IN9.IN4.Phase), digits = 3))))+
  theme(legend.position = "bottom")+
  labs(x = "")+
  xlim(0, 3),

ggplot(d[round(seq(1, to = nrow(d), length.out = 1000), digits = 0), ])+
  geom_path(aes(x = Time, y = IN4, color = as.factor(round(IN4.Corr, digits = 3)), group = 1))+
  geom_path(aes(x = Time, y = IN9, color = as.factor(round(IN9.Corr, digits = 3)), group = 1))+
  theme(legend.position = "bottom")+
  labs(x = "")+
  xlim(0, 3),

ggplot(d[round(seq(1, to = nrow(d), length.out = 1000), digits = 0), ])+
  geom_path(aes(x = Time, y = IN4, color = as.factor(round(IN4.Corr.All, digits = 3)), group = 1))+
  geom_path(aes(x = Time, y = IN9, color = as.factor(round(IN9.Corr.All, digits = 3)), group = 1))+
  theme(legend.position = "bottom")+
  labs(x = "")+
  xlim(0, 3)

), ncol = 1)

return(plts)
})

```

```{r eval=FALSE, include=FALSE}
walk(seq_along(my.plots), function(i){
  ggsave(paste0("plt", as.character(i), ".tiff"), plot = my.plots[[i]], path = "C:/Users/drk8b9/Desktop/rm_output/")
})


```











# Discarded

```{r eval=FALSE, include=FALSE}
# backup <- d
d <- backup
```


```{r eval=FALSE, include=FALSE}





# ggplot(d[d$Time>8 &
#            d$Time<11, ], aes(x = Time, y = event2, color = event2))+
#   geom_point()+
#   geom_line(aes(x = Time, y = IN9+40))+
#   geom_hline(yintercept = -35+40)
# 
# d[d$Time>2 &
#            d$Time<5, "event2"] %>% unique()
# # Make Bursts
# # DlgCreate ("Find bursts");						'creates dialog to assign channels, the maximum interval spikes are allowed to have to still
# # DlgChan (1,"Input channel", 2);				'belong to one burst and the minimum number of spikes that can make up a burst. maximum interval
# # DlgChan (2, "Output channel", 128);			'can be set seperately for the first two spikes in a burst.
# # DlgString (3, "Name of new channel", 20);
# # DlgReal (4, "Maximum spike interval", 0,100);
# # DlgReal (5, "Maximum spike interval for first 2 events", 0,100);
# # DlgReal (6, "Minimum number of events", 2,100);
# # DlgReal (7, "Minimum burst duration", 0, 100);
# # DlgCheck(8,"allow single spike bursts");
# 
# max.spike.interval <- 1
# max.spike.interval.first2 <- 1
# min.num.events <- 2
# min.burst.duration <- 0.1
# allow.single.spikes <- F
# 
# 
# 
# 
# 
# # Burst Statistics
# # 'The values printed to the log window are:
# # 
# # '"burst": this numbers the bursts from 1 to n. can be corrected by adding or substracting after checking the box in the dialog.
# # 'maybe useful if your file is one of a series of files from the same experiment. again, keep in mind that the last burst of the
# # 'last data file was omitted! you may want to add the number of the last burst in the last data file +1!
# # 
# # '"startT [s]": this gives the absolute start time of every burst, based on the time base of the data file.
# # 
# # '"endT [s]": this gives the absolute end time of every burst, based on the time base of the data file.
# # 
# # '"relative startT [s]": this, by default, substracts the time value of cursor 1 (if present) from the absolute time, so your
# # 'analysis starts at 0. if you check the box in the dialog you can add or substract to match the time code of a preceeding or
# # 'following data file from the same experiment.
# # 
# # '"relative endT [s]": see above.
# # 
# # '"cycle period [s]": returns time from one burst start to the next.
# # 
# # '"inst burstfreq [Hz]": inverse of the cycle period.
# # 
# # '"duration [s]": returns time from burst start to burst end.
# # 
# # '"dutycycle": returns duration/cycle period.
# # 
# # '"#spikes": counts the number of spikes within a burst.
# # 
# # '"spikefreq in burst [Hz]": returns #spikes/duration.
# # 
# # 'filename, channel assignments and start and end times are printed as a header. you may want to delete them before saving as text and
# # 'importing into a statistics or plot program.
# # 
# # 'dirk bucher, january 2002.
# # 'bug fix 06/09/03	--> spkfreq in burst is now calculated as nspk-1/dur

```


## working off of extracellular

```{r eval=FALSE, include=FALSE}
ggplot(d)+
  geom_line(aes(x = Time, y = IN14), color = "steelblue")+
  geom_line(aes(x = Time, y = IN15), color = "firebrick")


```


