---
title: "02.2Refactor"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## General ====
library("tidyverse") # Plotting and data manipulation
library(here)

## Statistics ====
library(drc) # for asymptotic model
# library("nlme") # for nested anova via lme. See http://www.jason-french.com/tutorials/repeatedmeasures.html
# library("multcomp")
# library("car")
# library("agricolae")
# library(bayestestR)
# # library(rstanarm)
# library(estimate)
# library(equivalence)
#
#
# ## Plotting ====
library(patchwork)
# library("cowplot") # clean up ggplots, plotgrid
# library("ggthemes")
library("lemon")
# library(Hmisc) # for mean_sdl ribbons
# library("ggthemes")
# library("ggsci")
# library(see) # Utrum damnati futuri sint, qui non viderunt et crediderunt
# library(patchwork)
#
# ## Specialty functions ====
source(here("R", "02MoniterGapJunction.R"))
#
# ## Global Params ====
# # theme_set(kickme())
# theme_set(theme_minimal())
# library(broom) # for parameter estimates
# library("furrr")
# plan(multiprocess)
```

# Read in and aggregate data
```{r read in data, eval=TRUE, include=FALSE}
# Preprocessing ----
tecc <- readRDS(file = here("data", "tecc.rds"))
tevc <- readRDS(file = here("data", "tevc.rds"))

tecc <- collapse_duplicate_gj_obs(tecc)
tevc <- collapse_duplicate_gj_obs(tevc)

## Join independent data types into a single data frame ====
all.data <- full_join(tecc, tevc)

all.data <- all.data[, c(
  "Condition", "Experiment", "Time", "Inj_Cell",
  "tecc.recording", "tevc.recording",
  "r11", "r12", "r1", "rc", "cc", "rmp", "gj"
)]

all.data <- all.data %>% as.data.frame()
```

```{r}
## Rename conditions ====
rename.df <- as.data.frame(list(
  c("Aberrant Depol", "PS.0.High.Amp"),
  c("Aberrant_Depol_22.5_deg", "PS.22.High.Amp"),

  c("HA 90 Degree", "PS.90.HA"),
  c("HA 90 Degree Cd", "PS.90.HA.Cd"),

  c("0_deg", "PS.0"),
  c("22.5_degrees", "PS.22"),
  c("rep 45 Degree", "PS.45"),
  c("rep 90 Degree", "PS.90"),

  c("PS.0.orig", "PS.0.orig"),
  c("PS.22.orig", "PS.22.orig"),
  c("PS.45.orig", "PS.45.orig"),
  c("PS.90.orig", "PS.90.orig"),
  c("PS.180.orig", "PS.180.orig"),

  c("hold_at_-53mV", "Silent.53mV"),
  c("TEA_ControlWave", "PS.0.TEA"),
  c("PS.0.TEA", "PS.0.TEA"),
  c("TEA_Silent", "Silent.TEA"),
  c("Inverted Wave", "Inv"),

  c("TEA.Active", "TEA.Active")
))

rename.df <- as.data.frame(t(rename.df))
names(rename.df) <- c("old", "new")
rownames(rename.df) <- NULL # get rid of rownames

all.data$changed <- F
for (i in seq(1, nrow(rename.df))){
  all.data[all.data$Condition == as.character(rename.df[i, "old"]), "Condition"] <- as.character(rename.df[i, "new"])
  all.data[all.data$Condition == as.character(rename.df[i, "old"]), "changed"] <- T
}
# print out the unchanged rows
print(all.data[!all.data$changed & !(all.data$Condition %in% as.vector(rename.df[, "new"])), ])
#and drop
all.data <- all.data[, !(names(all.data) %in% c("changed"))]

# reorder factors
all.data$Condition <- factor(all.data$Condition, as.vector(rename.df[, "new"])[-16] ) #-16 removes the duplicate "PS.0.TEA

#convert gj to inverse to make it easier to work with.
all.data$gj <- (1/all.data$gj)
```

```{r}
# restrict to the final set of conditions:
all.data <- all.data[all.data$Condition %in% c(
  "PS.0.High.Amp", "PS.22.High.Amp",
  "PS.90.HA", "PS.90.HA.Cd",
  "PS.0", "PS.22", "PS.45", "PS.90"), ]
```

```{r}
# new qc, flag first then remove.
# this allows for visualization before removal.
dept.vars = c("r11", "r12", "r1", "rc", "cc", "rmp", "gj")

for( dept.var in dept.vars){
  QC.var = paste0("QC", dept.var)
  all.data[QC.var] = FALSE

  ### 1. Resistances can't be zero, drop any which are.  ####
  if(dept.var %in% c("r11", "r12", "r1", "rc", #"cc", "rmp",
                     "gj")){
    mask <- (!is.na(all.data[dept.var]) & (all.data[dept.var] < 0))
    all.data[mask, QC.var] = TRUE
  }
  ### 2. If coupling coef is less than 0 or above 1, drop it. ####
  if(dept.var %in% c("cc")){
    mask <- (!is.na(all.data[dept.var]) & (all.data[dept.var] > 1 | all.data[dept.var] < 0))
    all.data[mask, QC.var] = TRUE
  }
}

# # for condition | time | response var
# conditions <- all.data$Condition %>% unique()
# times <- all.data$Time %>% unique()
# response.vars <- c("r11", "r1", "cc", "a.peak.nA", "htk.peak.nA", "rc", "gj")
#
# multiplier <-  2
# use.method <- "use.sd" #use.iqr
#
# tic <- Sys.time()
# for (i in seq_along(conditions)) {
#   for (j in seq_along(times)) {
#     for (k in seq_along(response.vars)) {
#       if (use.method == "use.sd") {
#         current.mean <- all.data[all.data$Condition == conditions[i] &
#           all.data$Time == times[j], response.vars[k]] %>% mean(na.rm = TRUE)
#         current.sd <- all.data[all.data$Condition == conditions[i] &
#           all.data$Time == times[j], response.vars[k]] %>% sd(na.rm = TRUE)
#
#         all.data[all.data$Condition == conditions[i] & all.data$Time == times[j] & ((all.data[[response.vars[k]]] < (current.mean - (multiplier * current.sd))) | (all.data[[response.vars[k]]] > (current.mean + (multiplier * current.sd)))) & !(is.na(all.data[[response.vars[k]]])), response.vars[k]] <- NA
#       } else if (use.method == "use.iqr") {
#         current.median <- all.data[all.data$Condition == conditions[i] &
#           all.data$Time == times[j], response.vars[k]] %>% median(na.rm = TRUE)
#         current.iqr <- all.data[all.data$Condition == conditions[i] &
#           all.data$Time == times[j], response.vars[k]] %>% IQR(na.rm = TRUE)
#
#         all.data[all.data$Condition == conditions[i] & all.data$Time == times[j] & ((all.data[[response.vars[k]]] < (current.median - (multiplier * current.iqr))) | (all.data[[response.vars[k]]] > (current.median + (multiplier * current.iqr)))) & !(is.na(all.data[[response.vars[k]]])), response.vars[k]] <- NA
#       } else {
#         warning(paste(as.character(use.method), "is not use.sd or use.iqr!"))
#       }
#     }
#   }
# }
# print(Sys.time() - tic)

```





### Reduce dataset
```{r}
# Reduce data to target times ----
# all.data <- all.data[all.data$Time %in% c(0, 20, 40, 60), ]

```

### Calculate deltas and percent changes
```{r}
all.data.d <- convert_data_to(
  input.df = all.data,
  convert.to = c("difference"),
  data.cols = c("r11", "r12", "r1", "rc", "cc", "rmp", "gj"
  )
)

M <- all.data#[all.data$Time %in% c(0, 20, 40, 60) , ]
M.d <- all.data.d#[all.data.d$Time %in% c(0, 20, 40, 60) , ]
```

## Test w/o deltas
```{r}
# d <- add_stim_delay_phase(d = M)
# d <- M
#
# d$inter <- paste0(d$Experiment, ".", d$Inj_Cell)
# # REPEAT Manual QC wonky points ----
# ## gj ====
# #TEA sync
# d[d$inter == "180212.LC4" & d$Time %in% c(40), "gj"] <- NA
# # ps0
# d[d$inter == "180507.LC4" & d$Time %in% c(40), "gj"] <- NA
#
# ## rc ====
# # ps0
# d[d$inter == "180507.LC4" & d$Time %in% c(40), "rc"] <- NA
# # PS.22
# d[d$inter == "181001.LC4" & d$Time %in% c(40, 60), "rc"] <- NA

```

```{r}
# Use expand grid to get a full combination of tests then filter out the ones we don't want. This will let us use one future_map and maybe get faster
comparisons <- c(paste("PS.0.High.Amp", "PS.22.High.Amp", sep = "_"),
                 paste("PS.22.High.Amp", "PS.90.HA", sep = "_"),
                 paste("PS.90.HA", "PS.90.HA.Cd", sep = "_"),
                 paste("PS.0", "PS.22", "PS.45", "PS.90", sep = "_"))
dept.vars <- c("gj",
               "rc",
               "r12",
               "cc",
               "rmp",
               "r11",
               "r1")

# Set up a df with the inputs I want.
all.tests <- as.data.frame(expand.grid(comparisons, dept.vars))
names(all.tests) <- c("Groups", "DV")

# all.tests <- all.tests %>%
#   mutate(Obs.Net = ifelse(DV %in% c("gj", "Rc", "rc", "r12"), T, F)) %>% #NOTE: gj == Rc; gj != rc
#   mutate(Model = ifelse(Groups == "PS.90.HA", "dept.var ~ Time", "dept.var ~ Time * Condition")) %>% #TODO switch to a more robust   mutate(Random = "~1 | Experiment")
```

template for one
```{r}
# Test ----
d <- M
M.clean <- d #%>% rename(Rc = gj)
```

# figures explicit
```{r}
condition.labs <- c("TEA Mimic Sync", "TEA Mimic Async", "Depol. Async", "Depol. Async Cd2+",
                    "Standardized \n0 Deg.", "Standardized \n22.5 Deg.", "Standardized \n45 Deg.", "Standardized \n90 Deg.",
                    "Individualized \n0 Deg.", "Individualized \n22.5 Deg.", "Individualized \n45 Deg.", "Individualized \n90 Deg.", "Individualized \n180 Deg.")

names(condition.labs) <- c("PS.0.High.Amp", "PS.22.High.Amp", "PS.90.HA", "PS.90.HA.Cd",
                           "PS.0", "PS.22", "PS.45", "PS.90",
                           "PS.0.orig", "PS.22.orig", "PS.45.orig", "PS.90.orig", "PS.180.orig")

M.clean$Condition <- factor(M.clean$Condition, levels = c("PS.0.High.Amp", "PS.22.High.Amp", "PS.90.HA", "PS.90.HA.Cd",
                                                          "PS.0", "PS.22", "PS.45", "PS.90",
                                                          "PS.0.orig", "PS.22.orig", "PS.45.orig", "PS.90.orig", "PS.180.orig"))

### Params ####
text.size = 20
point.size = 3
line.size = 3
mean.point.size = 3
mean.line.size = 3

### High Amplitude Plots ####
plt.tea <- M.clean[M.clean$Condition %in% c("PS.0.High.Amp", "PS.22.High.Amp"), ] %>%
  dplyr::select(Condition, Experiment, Inj_Cell, Time, gj) %>%
  group_by(Condition, Experiment, Inj_Cell, Time) %>%
  summarise(gj = mean(gj, na.rm = T)) %>%
  ungroup() %>%
  # mutate(Time = as.character(Time)) %>%
  pivot_wider(names_from = Time, values_from = gj) %>%
  mutate(`20` = `20` - `0`,
         `40` = `40` - `0`,
         `60` = `60` - `0`) %>%
  mutate(`0` = 0) %>%
  pivot_longer(cols = c(`0`, `20`, `40`, `60`), names_to = "Time", values_to = "gj") %>%
  group_by(Condition, Time) %>%
  mutate(mean_gj = mean(gj, na.rm = T),
         mean_sd_up = mean_gj+sd(gj, na.rm = T),
         mean_sd_dn =mean_gj- sd(gj, na.rm = T),) %>%
  mutate(inter = paste(Experiment, Inj_Cell, sep = ".")) %>%
  ggplot(aes(x = Time,
             y = gj,
             # color = Experiment,
             # shape = Inj_Cell,
             group = inter))+
  geom_ribbon(aes(ymin=mean_sd_dn, ymax=mean_sd_up), fill = "gray", alpha = 0.1)+
  lemon::geom_pointline(size = point.size, linesize = line.size)+
  geom_point(aes(x = Time, y = mean_gj), color = "white", size = mean.point.size, alpha = 0.3)+
  geom_pointline(aes(x = Time, y = mean_gj), color = "firebrick", size = mean.point.size, linesize = mean.line.size,  shape = 1)+
  labs(y = expression(paste(Delta, "Rc", " in M", Omega)), x = "Time in Minutes")+
  facet_grid(.~Condition,
             labeller = labeller(Condition = condition.labs))+
  geom_hline(yintercept = 0)+
  theme(
    # axis.text = element_text(size = rel(2), angle = 0),
        text = element_text(size=text.size)
        )

plt.hv <- M.clean[M.clean$Condition %in% c("PS.90.HA", "PS.90.HA.Cd" ), ] %>%
  dplyr::select(Condition, Experiment, Inj_Cell, Time, gj) %>%
  group_by(Condition, Experiment, Inj_Cell, Time) %>%
  summarise(gj = mean(gj, na.rm = T)) %>%
  ungroup() %>%
  # mutate(Time = as.character(Time)) %>%
  pivot_wider(names_from = Time, values_from = gj) %>%
  mutate(`20` = `20` - `0`,
         `40` = `40` - `0`,
         `60` = `60` - `0`) %>%
  mutate(`0` = 0) %>%
  pivot_longer(cols = c(`0`, `20`, `40`, `60`), names_to = "Time", values_to = "gj") %>%
  group_by(Condition, Time) %>%
  mutate(mean_gj = mean(gj, na.rm = T),
         mean_sd_up = mean_gj+sd(gj, na.rm = T),
         mean_sd_dn =mean_gj- sd(gj, na.rm = T),) %>%
  mutate(inter = paste(Experiment, Inj_Cell, sep = ".")) %>%
  ggplot(aes(x = Time,
             y = gj,
             # color = Experiment,
             # shape = Inj_Cell,
             group = inter))+
  geom_ribbon(aes(ymin=mean_sd_dn, ymax=mean_sd_up), fill = "gray", alpha = 0.1)+
  lemon::geom_pointline(size = point.size, linesize = line.size)+
  geom_point(aes(x = Time, y = mean_gj), color = "white", size = mean.point.size, alpha = 0.3)+
  geom_pointline(aes(x = Time, y = mean_gj), color = "firebrick", size = mean.point.size, linesize = mean.line.size,  shape = 1)+
  labs(y = expression(paste(Delta, "Rc", " in M", Omega)), x = "Time in Minutes")+
  facet_grid(.~Condition,
             labeller = labeller(Condition = condition.labs))+
  geom_hline(yintercept = 0)+
  theme(
    # axis.text = element_text(size = rel(2), angle = 0),
        text = element_text(size=text.size)
        )




### Low Voltage plots ####
plt.lv <- M.clean[M.clean$Condition %in% c("PS.0", "PS.22", "PS.45", "PS.90"), ] %>%
  dplyr::select(Condition, Experiment, Inj_Cell, Time, gj) %>%
  group_by(Condition, Experiment, Inj_Cell, Time) %>%
  summarise(gj = mean(gj, na.rm = T)) %>%
  ungroup() %>%
  # mutate(Time = as.character(Time)) %>%
  pivot_wider(names_from = Time, values_from = gj) %>%
  mutate(`20` = `20` - `0`,
         `40` = `40` - `0`,
         `60` = `60` - `0`) %>%
  mutate(`0` = 0) %>%
  pivot_longer(cols = c(`0`, `20`, `40`, `60`), names_to = "Time", values_to = "gj") %>%
  group_by(Condition, Time) %>%
  mutate(mean_gj = mean(gj, na.rm = T),
         mean_sd_up = mean_gj+sd(gj, na.rm = T),
         mean_sd_dn =mean_gj- sd(gj, na.rm = T),) %>%
  mutate(inter = paste(Experiment, Inj_Cell, sep = ".")) %>%
  ggplot(aes(x = Time,
             y = gj,
             # color = Experiment,
             # shape = Inj_Cell,
             group = inter))+
  geom_ribbon(aes(ymin=mean_sd_dn, ymax=mean_sd_up), fill = "gray", alpha = 0.1)+
  lemon::geom_pointline(size = point.size, linesize = line.size)+
  geom_point(aes(x = Time, y = mean_gj), color = "white", size = mean.point.size, alpha = 0.3)+
  geom_pointline(aes(x = Time, y = mean_gj), color = "firebrick", size = mean.point.size, linesize = mean.line.size,  shape = 1)+
  labs(y = expression(paste(Delta, "Rc", " in M", Omega)), x = "Time in Minutes")+
  facet_grid(.~Condition,
             labeller = labeller(Condition = condition.labs))+
  geom_hline(yintercept = 0)+
  theme(
    # axis.text = element_text(size = rel(2), angle = 0),
        text = element_text(size=text.size)
        )
```



# Functions for plotting/reporting
```{r}
mk_annotated_delta_df <- function(
all.data = all.data,
# what is the largest change in 20 minutes that we're willing to accept as real?
# to be useful this might be something on the order of 1.5 but can be set high
# to use only threshold change on the residual relative to the median.
threshold_change = 21.4,  
# relative to the median.
threshold_change_res = 1.5,
ith_condition = c("PS.0", "PS.22", "PS.45", "PS.90")
){
# # inputs
# all.data = all.data
# threshold_change = 21.4  #1.5 #
# threshold_change_res = 1.5
# ith_condition = c("PS.0", "PS.22", "PS.45", "PS.90")
  
## Calculate baseline, deltas ==================================================
temp <- all.data %>% dplyr::select(Condition, Experiment, Inj_Cell, Time, gj)

# Get baseline values so we can easily replace with deltas
temp.t0 <- temp %>%
  dplyr::filter(Time == 0) %>%
  rename(initial = gj) %>%
  dplyr::select(-Time)

temp <- full_join(temp, temp.t0)
temp$gj = temp$gj - temp$initial

temp$Time <- as.numeric(temp$Time)

# reduce down to target conditions
temp_2 <- temp[temp$Condition %in% c(ith_condition), ]

# Check if there's an 80 minute time point. calculate delta accordingly
if (80 %in% unique(temp_2$Time) ){
  # Get stepwise change
  temp_2_diff = temp_2 %>% 
    pivot_wider(names_from =  Time, values_from = gj) %>% 
    mutate(delta00 = 0,
           delta20 = `20`-`0`,
           delta40 = `40`-`20`,
           delta60 = `60`-`40`,
           delta80 = `80`-`60`
           ) %>% 
    pivot_longer(c(delta00, delta20, delta40, delta60
                   , delta80
                   ), 
                 names_to = "dTime", values_to = "diffgj") %>% 
    dplyr::select(Condition, Experiment, Inj_Cell, dTime, diffgj) %>% 
    mutate(Time = as.numeric(str_remove(dTime, "delta"))) %>% 
    dplyr::select(-dTime)
} else {
  temp_2_diff = temp_2 %>% 
    pivot_wider(names_from =  Time, values_from = gj) %>% 
    mutate(delta00 = 0,
           delta20 = `20`-`0`,
           delta40 = `40`-`20`,
           delta60 = `60`-`40`
           ) %>% 
    pivot_longer(c(delta00, delta20, delta40, delta60
                   ), 
                 names_to = "dTime", values_to = "diffgj") %>% 
    dplyr::select(Condition, Experiment, Inj_Cell, dTime, diffgj) %>% 
    mutate(Time = as.numeric(str_remove(dTime, "delta"))) %>% 
    dplyr::select(-dTime)  
}

temp_2 = full_join(temp_2, temp_2_diff)


## Calculate selection metrics =================================================
# Try adding in residual from groupxtime change
temp_2 <- temp_2 %>%
  ungroup() %>%
  group_by(Condition, Time) %>%
  mutate(median_gj = median(gj, na.rm = T)) %>%
  mutate(residual_gj = median_gj - gj) %>%
  ungroup()

temp_2["absdiffgj"] <- abs(temp_2$diffgj)
temp_2["absresidgj"] <- abs(temp_2$residual_gj)


## Flag all points after an offending observation ==============================
temp_2["remove"] = FALSE
temp_2 <- temp_2[!is.na(temp_2$gj), ]
temp_2 <- temp_2[!is.na(temp_2$absdiffgj), ]
temp_2[temp_2$absdiffgj > threshold_change, "remove"] = TRUE
# and add in residual
temp_2[temp_2$absresidgj > threshold_change_res, "remove"] = TRUE

temp_2$Condition <- as.character(temp_2$Condition)
# flag everything after the first deviation
# assume that if an experiment fails, every time point after it is not to be trusted.
flag_after <- temp_2[temp_2$remove, ]
if(nrow(flag_after >= 1)){
  for(i in seq(1, nrow(flag_after))){
   mask <- (temp_2$Condition == unlist(flag_after[i, "Condition" ])
       ) & (temp_2$Experiment == unlist(flag_after[i, "Experiment" ])
       ) & (temp_2$Inj_Cell == unlist(flag_after[i, "Inj_Cell" ])
       ) & (temp_2$Time >= unlist(flag_after[i, "Time"]))
  
    temp_2[mask, "remove"] <- TRUE 
  }
}


## =============================================================================

return(temp_2)
  
}

# summary and diagnostics 
# diagnostic plot --------------------------------------------------------------
annotated_delta_df_diagnostic <- function(df,
                              threshold_change_res = 1.5){
  temp_2 <- df
  plt <- temp_2 %>% 
    ggplot(aes(Time, gj, color = remove))+
    geom_ribbon(aes(ymin=median_gj-threshold_change_res, 
                    ymax=median_gj+threshold_change_res), 
                fill = "gray", color = "black", alpha = 1)+
    geom_line(aes(y = median_gj), color = "black", size = 1)+
    geom_hline(yintercept = 0)+
    geom_point()+
    geom_point(shape = 1, color = 'black')+
    geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
    facet_grid(.~Condition)+
    theme(legend.position = 'bottom')
  return(plt)
}



get_grouped_iqrs <- function(df = temp_2){
  df %>% 
    group_by(Condition, Time) %>% 
    summarize(iqr = IQR(gj, na.rm = T)) %>% 
    pivot_wider(id_cols = Condition, 
                names_from = Time, 
                values_from = iqr)  
}

# get groupwise iqr, summarize at time points
get_grouped_iqrs_collapse_to_time <- function(df = temp_2){
  df %>% 
    group_by(Condition, Time) %>% 
    summarize(iqr = IQR(gj, na.rm = T)) %>% 
    ungroup() %>% 
    group_by(Time) %>% 
    summarize(
      min_iqr  = min(iqr, na.rm = T),
      mean_iqr = mean(iqr, na.rm = T),
      max_iqr  = max(iqr, na.rm = T) )   
}



# Models to compare ------------------------------------------------------------
## Full model
mk_asymptotic_model <- function(
  df = temp_2,
  apply_qc = TRUE
){
  if(apply_qc){
    # fit model with condition affecting intercept but not time constant
    fm <- drm(gj ~ Time, Condition,
            data = df[!df$remove,],
            fct = AR.2(),
            pmodels = list(~factor(Condition), 
                           ~1))
  } else {
    # This is expected to fail in some cases. Not intended to be used.
    fm <- drm(gj ~ Time, Condition,
          data = df,
          fct = AR.2(),
          pmodels = list(~factor(Condition), 
                         ~1))
  }
  return(fm)
}

## Reduced Model
mk_reduced_asymptotic_model <- function(
    df = temp_2,
  apply_qc = TRUE
){
  if(apply_qc){
    # fit model with condition affecting intercept but not time constant
    fm <- drm(gj ~ Time, Condition,
            data = df[!df$remove,],
            fct = AR.2(),
            pmodels = list(~1, 
                           ~1))
  } else {
    # This is expected to fail in some cases. Not intended to be used.
    fm <- drm(gj ~ Time, Condition,
          data = df,
          fct = AR.2(),
          pmodels = list(~1, 
                         ~1))
  }
  return(fm)
}


# Compare Models ---------------------------------------------------------------
# returns anova table, d effect table
mk_tables <- function(fm, fm_reduced){
  # is using the treatment effect justified?
  ares <- anova(fm, fm_reduced) # note that the "1st" model is not the first one
                                # input but the simpler one.
  ares_p <- ares[2, 'p value']
  if(ares_p < 0.05){
    print("P < 0.05")
  } else {
    print("Warning P >= 0.05")
  }
  
  fmres <- compParm(fm, "d")
  
  return(list(ares, fmres))
}

# wrap mk tables and save out stats
write_out_fm_res <- function(fm = fm, 
                             fm_reduced = fm_reduced,
                             save_suffix = ""){
  res <- mk_tables(fm, fm_reduced)
  main_effect <- res[[1]]
  compare_d <- res[[2]]
  write.csv(main_effect, file = paste0("./a_reg_main_", save_suffix, ".csv"))
  write.csv(compare_d,   file = paste0("./a_reg_d_",    save_suffix, ".csv"))
  return(list(main_effect, compare_d))
}



#fcn that takes fm, time and returns predictions
mk_fm_plotting_df <- function(df = temp_2, 
                              fm = fm){
  fm_line <- data.frame(expand.grid(
  Time = seq(0, max(df$Time, na.rm = TRUE), by  = 1), 
  Condition = unique(df$Condition) 
  ))

  fm_line <- cbind(fm_line, predict(fm, newdata = fm_line, se.fit = TRUE))
  # SE is only provided once, apply to rest of data.
  fm_line_se <- fm_line[!is.na(fm_line$SE), c('Time', 'SE')]
  fm_line <- fm_line %>% dplyr::select(-SE)
  fm_line <- full_join(fm_line, fm_line_se)
  return(fm_line)
}



#fcn that takes predictions, data and plots a second diagnostic
# this is what will be tweaked to be the final plot
delta_df_prediction_plot <- function(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions
){
  if(apply_qc){
    df <- df[!df$remove,]  
  }
  # sem lower and upper
  predictions['SEML'] <-   predictions['Prediction'] - predictions['SE']
  predictions['SEMU'] <-   predictions['Prediction'] + predictions['SE']  
  
  ### Does the fit look reasonable?
  plt <- df %>% 
    ggplot(aes(Time))+ #, color = remove))+
    geom_hline(yintercept = 0)+
    geom_ribbon(data = predictions, aes(ymin=SEML, ymax=SEMU), 
                fill = "gray", color = "black", alpha = 1)+
    geom_point(aes(y=gj))+
    geom_line(aes(y=gj, group = interaction(Experiment, Inj_Cell)))+
    geom_line(data = predictions, aes(y = Prediction), color = 'red', size = 1)+
    facet_grid(.~Condition)
  
  return(plt)
}



# extends delta_df_prediction_plot to have similar aes to the previous plot set.
# bands are sd 
# red lines are predition and sem
delta_df_publication_plot <- function(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = expression(paste(Delta, "gj"^-1, " in M", Omega))
){
  # df = temp_2
  # apply_qc = TRUE
  # predictions = predictions
  # 
  # text.size = 20
  # point.size = 2
  # line.size = 3
  # mean.point.size = 2
  # mean.line.size = 2
  # ylab_expression = expression(paste(Delta, "gj"^-1, " in M", Omega))
  
  
  if(apply_qc){
    df <- df[!df$remove,]  
  }
  # sem lower and upper
  predictions['SEML'] <-   predictions['Prediction'] - predictions['SE']
  predictions['SEMU'] <-   predictions['Prediction'] + predictions['SE']  
  
  
  # keep line form extending past data
  
  for (condition in unique(df$Condition)){
    condition_max_time = max( df[df$Condition == condition, 'Time'], na.rm = TRUE)
    mask <- (predictions$Condition != condition
             ) | ((predictions$Condition == condition
              ) & (predictions$Time <= condition_max_time)) 
    
    predictions <- predictions[mask, ]
  }
  
  
  summary_stats <- df %>% 
    group_by(Condition, Time) %>% 
    summarise(mean = mean(gj, na.rm = T),
              median = median(gj, na.rm = T),
              iqr = IQR(gj, na.rm = T),
              sd = sd(gj, na.rm = T)) %>% 
    ungroup() %>% 
    mutate(mean_up = mean +sd,
           mean_do = mean -sd,
           med_up = median+iqr, # TODO do we want to show 1 or 1/2?
           med_do = median-iqr)
  
  
  ### Does the fit look reasonable?
  plt <- df %>% 
    ggplot(aes(Time))+ #, color = remove))+
    geom_hline(yintercept = 0)+
    ## Bands ==============================================================
    geom_ribbon(data = summary_stats, aes(ymin=mean_do, ymax=mean_up), 
                fill = "cornflowerblue", 
                #color = "cornflowerblue", 
                alpha = 0.3)+
    
    geom_line(data = predictions, aes(y = Prediction), 
            color = 'firebrick', size = 1, alpha = 0.5)+
    geom_line(data = predictions, aes(y = SEML), 
            color = 'firebrick', size = 1, alpha = 0.5, linetype = 'dashed')+
    geom_line(data = predictions, aes(y = SEMU), 
            color = 'firebrick', size = 1, alpha = 0.5, linetype = 'dashed')+
  
    
    # geom_ribbon(data = summary_stats, aes(ymin=med_do, ymax=med_up),   # median
    #             fill = "blue", color = "blue", alpha = 0.51)+
    # geom_ribbon(data = predictions, aes(ymin=SEML, ymax=SEMU), # model
    #             fill = "cornflowerblue", color = "cornflowerblue", alpha = 0.3)+
  
    ## data ======================================================================
    # geom_point(aes(y=gj))+
    # geom_line(aes(y=gj, group = interaction(Experiment, Inj_Cell)))+
    lemon::geom_pointline(aes(y=gj, group = interaction(Experiment, Inj_Cell)),
                          color = "cornflowerblue", size = point.size, 
                          linesize = line.size, alpha = 0.5)+
    
    # geom_point(data = summary_stats, aes(x = Time, y = mean), 
    #            color = "white", size = mean.point.size, alpha = 0.3)+
    # geom_pointline(data = summary_stats, aes(x = Time, y = mean), 
    #                color = "firebrick", size = mean.point.size, 
    #                linesize = mean.line.size,  shape = 1)+
    
    ## lines =====================================================================
    # # mean
    # geom_line(data = summary_stats, aes(y = mean), 
    #           color = 'cornflowerblue', size = 1)+
    # # median
    # geom_line(data = summary_stats, aes(y = median), 
    #           color = 'blue', size = 1)+
    # 
  
    
    facet_grid(.~Condition, labeller = labeller(Condition = condition.labs))+
    labs(y = ylab_expression, x = "Time in Minutes")+
    # facet_grid(.~Condition,
              
    geom_hline(yintercept = 0)+
    theme(
      # axis.text = element_text(size = rel(2), angle = 0),
          text = element_text(size=text.size)
          )
  return(plt)
}

```


# Delta GJ Statistics
## TEA
```{r}
savename = "TEAMimic"

temp_2 <- mk_annotated_delta_df(
  all.data = all.data,
  threshold_change = 100.07,     # 
  threshold_change_res = 1.63, # <- max groupwise collapsed iqr
  ith_condition = c("PS.0.High.Amp",  "PS.22.High.Amp")
)


# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

get_grouped_iqrs_collapse_to_time(df = temp_2)

plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = 1.5)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)


predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = expression(paste(Delta, "gj"^-1, " in M", Omega))
  
)

plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = 7.14, height = 5.81, units = "in")
       # width = 10.68, height = 5.81, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = 7.14, height = 5.81, units = "in")
       # width = 10.68, height = 5.81, units = "in")


```


## ha (actual)
```{r}
savename = "HighAmpCd"

temp_2 <- mk_annotated_delta_df(
  all.data = all.data,
  threshold_change = 100.07,     # 
  threshold_change_res = 1.23, # <- max groupwise collapsed iqr
  ith_condition = c("PS.90.HA", "PS.90.HA.Cd")
)




# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

get_grouped_iqrs_collapse_to_time(df = temp_2)

plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = 1.5)

fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)

predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)

plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = expression(paste(Delta, "gj"^-1, " in M", Omega))
  
)

plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = 7.14, height = 5.81, units = "in")
       # width = 10.68, height = 5.81, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = 7.14, height = 5.81, units = "in")
       # width = 10.68, height = 5.81, units = "in")
```

## standardized

```{r}
savename = "Standardized"

temp_2 <- mk_annotated_delta_df(
  all.data = all.data,
  threshold_change = 100.07,     # 
  threshold_change_res = 1.16, # <- max groupwise collapsed iqr
  ith_condition = c("PS.0", "PS.22", "PS.45", "PS.90")
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

get_grouped_iqrs_collapse_to_time(df = temp_2)

plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = 1.5)

fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)

predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)

plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 

plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = expression(paste(Delta, "gj"^-1, " in M", Omega))
  
)

plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       # width = 7.14, height = 5.81, units = "in")
       width = 10.68, height = 5.81, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       # width = 7.14, height = 5.81, units = "in")
       width = 10.68, height = 5.81, units = "in")
```


# Delta CC Statistics (begin wrapper)
## TEA
```{r}
YLAB_EXPRESSION = expression(paste(Delta, "CC"))


savename = "cc_TEAMimic"
threshold_change = 100.07    # 
threshold_change_res = 0.13 # <- max groupwise collapsed iqr
ith_condition = c("PS.0.High.Amp",  "PS.22.High.Amp")
ylab_expression = YLAB_EXPRESSION
width = 7.14
height = 5.81

# overwrite 'gj' with desired parameter
all.data_alias_gj <- all.data
all.data_alias_gj <- all.data_change_gj %>% 
  mutate(gj = cc)  # <------------------------------------------------------ !!!

# Boilerplate ------------------------------------------------------------------
temp_2 <- mk_annotated_delta_df(
  all.data = all.data_alias_gj,
  threshold_change = threshold_change,     # 
  threshold_change_res = threshold_change_res, # <- max groupwise collapsed iqr
  ith_condition = ith_condition
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

largest_timewise_iqr <- get_grouped_iqrs_collapse_to_time(df = temp_2)
largest_timewise_iqr
print("-- -- -- -- -- -- -- -- ")
print(as.character(max(largest_timewise_iqr$max_iqr)))
print("-- -- -- -- -- -- -- -- ")


plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = threshold_change_res)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)


predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = ylab_expression
  
)


plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = width, height = height, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = width, height = height, units = "in")
```


## High Amplitude
```{r}
savename = "cc_HighAmpCd"
threshold_change = 100.07    # 
threshold_change_res = 0.24  # <- max groupwise collapsed iqr
ith_condition = c("PS.90.HA", "PS.90.HA.Cd")
ylab_expression = YLAB_EXPRESSION
width = 7.14
height = 5.81

# overwrite 'gj' with desired parameter
all.data_alias_gj <- all.data
all.data_alias_gj <- all.data_change_gj %>% 
  mutate(gj = cc)  # <------------------------------------------------------ !!!

# Boilerplate ------------------------------------------------------------------
temp_2 <- mk_annotated_delta_df(
  all.data = all.data_alias_gj,
  threshold_change = threshold_change,     # 
  threshold_change_res = threshold_change_res, # <- max groupwise collapsed iqr
  ith_condition = ith_condition
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

largest_timewise_iqr <- get_grouped_iqrs_collapse_to_time(df = temp_2)
largest_timewise_iqr
print("-- -- -- -- -- -- -- -- ")
print(as.character(max(largest_timewise_iqr$max_iqr)))
print("-- -- -- -- -- -- -- -- ")


plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = threshold_change_res)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)


predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = ylab_expression
  
)


plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = width, height = height, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = width, height = height, units = "in")
```

## standardized

```{r}
savename = "cc_Standardized"
threshold_change = 100.07    # 
threshold_change_res = 0.25  # <- max groupwise collapsed iqr
ith_condition = c("PS.0", "PS.22", "PS.45", "PS.90")
ylab_expression = YLAB_EXPRESSION
width = 10.68
height = 5.81

# overwrite 'gj' with desired parameter
all.data_alias_gj <- all.data
all.data_alias_gj <- all.data_change_gj %>% 
  mutate(gj = cc)  # <------------------------------------------------------ !!!

# Boilerplate ------------------------------------------------------------------
temp_2 <- mk_annotated_delta_df(
  all.data = all.data_alias_gj,
  threshold_change = threshold_change,     # 
  threshold_change_res = threshold_change_res, # <- max groupwise collapsed iqr
  ith_condition = ith_condition
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

largest_timewise_iqr <- get_grouped_iqrs_collapse_to_time(df = temp_2)
largest_timewise_iqr
print("-- -- -- -- -- -- -- -- ")
print(as.character(max(largest_timewise_iqr$max_iqr)))
print("-- -- -- -- -- -- -- -- ")


plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = threshold_change_res)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)

# FIXME In sqrt(diag(varMat)) : NaNs produced
predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = ylab_expression
  
)


plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = width, height = height, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = width, height = height, units = "in")
```


# Delta r1 Statistics
## TEA
```{r}
YLAB_EXPRESSION = expression(paste(Delta, "r1"))


savename = "r1_TEAMimic"
threshold_change = 100.07    # 
threshold_change_res = 1.97 # <- max groupwise collapsed iqr
ith_condition = c("PS.0.High.Amp",  "PS.22.High.Amp")
ylab_expression = YLAB_EXPRESSION
width = 7.14
height = 5.81

# overwrite 'gj' with desired parameter
all.data_alias_gj <- all.data
all.data_alias_gj <- all.data_change_gj %>% 
  mutate(gj = r1)  # <------------------------------------------------------ !!!

# Boilerplate ------------------------------------------------------------------
temp_2 <- mk_annotated_delta_df(
  all.data = all.data_alias_gj,
  threshold_change = threshold_change,     # 
  threshold_change_res = threshold_change_res, # <- max groupwise collapsed iqr
  ith_condition = ith_condition
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

largest_timewise_iqr <- get_grouped_iqrs_collapse_to_time(df = temp_2)
largest_timewise_iqr
print("-- -- -- -- -- -- -- -- ")
print(as.character(max(largest_timewise_iqr$max_iqr)))
print("-- -- -- -- -- -- -- -- ")


plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = threshold_change_res)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)


predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = ylab_expression
  
)


plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = width, height = height, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = width, height = height, units = "in")
```


## High Amplitude
```{r}
savename = "r1_HighAmpCd"
threshold_change = 100.07    # 
threshold_change_res = 1.67  # <- max groupwise collapsed iqr
ith_condition = c("PS.90.HA", "PS.90.HA.Cd")
ylab_expression = YLAB_EXPRESSION
width = 7.14
height = 5.81

# overwrite 'gj' with desired parameter
all.data_alias_gj <- all.data
all.data_alias_gj <- all.data_change_gj %>% 
  mutate(gj = r1)  # <------------------------------------------------------ !!!

# Boilerplate ------------------------------------------------------------------
temp_2 <- mk_annotated_delta_df(
  all.data = all.data_alias_gj,
  threshold_change = threshold_change,     # 
  threshold_change_res = threshold_change_res, # <- max groupwise collapsed iqr
  ith_condition = ith_condition
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

largest_timewise_iqr <- get_grouped_iqrs_collapse_to_time(df = temp_2)
largest_timewise_iqr
print("-- -- -- -- -- -- -- -- ")
print(as.character(max(largest_timewise_iqr$max_iqr)))
print("-- -- -- -- -- -- -- -- ")


plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = threshold_change_res)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)


predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = ylab_expression
  
)


plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = width, height = height, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = width, height = height, units = "in")
```

## standardized

```{r}
savename = "r1_Standardized"
threshold_change = 100.07    # 
threshold_change_res = 3.66  # <- max groupwise collapsed iqr
ith_condition = c("PS.0", "PS.22", "PS.45", "PS.90")
ylab_expression = YLAB_EXPRESSION
width = 10.68
height = 5.81

# overwrite 'gj' with desired parameter
all.data_alias_gj <- all.data
all.data_alias_gj <- all.data_change_gj %>% 
  mutate(gj = r1)  # <------------------------------------------------------ !!!

# Boilerplate ------------------------------------------------------------------
temp_2 <- mk_annotated_delta_df(
  all.data = all.data_alias_gj,
  threshold_change = threshold_change,     # 
  threshold_change_res = threshold_change_res, # <- max groupwise collapsed iqr
  ith_condition = ith_condition
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

largest_timewise_iqr <- get_grouped_iqrs_collapse_to_time(df = temp_2)
largest_timewise_iqr
print("-- -- -- -- -- -- -- -- ")
print(as.character(max(largest_timewise_iqr$max_iqr)))
print("-- -- -- -- -- -- -- -- ")


plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = threshold_change_res)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)


predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = ylab_expression
  
)


plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = width, height = height, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = width, height = height, units = "in")
```

# Delta r11 Statistics 
## TEA
```{r}
YLAB_EXPRESSION = expression(paste(Delta, "r11"))


savename = "r11_TEAMimic"
threshold_change = 100.07    # 
threshold_change_res = 1.10 # <- max groupwise collapsed iqr
ith_condition = c("PS.0.High.Amp",  "PS.22.High.Amp")
ylab_expression = YLAB_EXPRESSION
width = 7.14
height = 5.81

# overwrite 'gj' with desired parameter
all.data_alias_gj <- all.data
all.data_alias_gj <- all.data_change_gj %>% 
  mutate(gj = r11)  # <------------------------------------------------------ !!!

# Boilerplate ------------------------------------------------------------------
temp_2 <- mk_annotated_delta_df(
  all.data = all.data_alias_gj,
  threshold_change = threshold_change,     # 
  threshold_change_res = threshold_change_res, # <- max groupwise collapsed iqr
  ith_condition = ith_condition
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

largest_timewise_iqr <- get_grouped_iqrs_collapse_to_time(df = temp_2)
largest_timewise_iqr
print("-- -- -- -- -- -- -- -- ")
print(as.character(max(largest_timewise_iqr$max_iqr)))
print("-- -- -- -- -- -- -- -- ")


plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = threshold_change_res)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)


predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = ylab_expression
  
)


plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = width, height = height, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = width, height = height, units = "in")
```


## High Amplitude
```{r}
savename = "r11_HighAmpCd"
threshold_change = 100.07    # 
threshold_change_res = 0.95  # <- max groupwise collapsed iqr
ith_condition = c("PS.90.HA", "PS.90.HA.Cd")
ylab_expression = YLAB_EXPRESSION
width = 7.14
height = 5.81

# overwrite 'gj' with desired parameter
all.data_alias_gj <- all.data
all.data_alias_gj <- all.data_change_gj %>% 
  mutate(gj = r11)  # <------------------------------------------------------ !!!

# Boilerplate ------------------------------------------------------------------
temp_2 <- mk_annotated_delta_df(
  all.data = all.data_alias_gj,
  threshold_change = threshold_change,     # 
  threshold_change_res = threshold_change_res, # <- max groupwise collapsed iqr
  ith_condition = ith_condition
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

largest_timewise_iqr <- get_grouped_iqrs_collapse_to_time(df = temp_2)
largest_timewise_iqr
print("-- -- -- -- -- -- -- -- ")
print(as.character(max(largest_timewise_iqr$max_iqr)))
print("-- -- -- -- -- -- -- -- ")


plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = threshold_change_res)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)


predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = ylab_expression
  
)


plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = width, height = height, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = width, height = height, units = "in")
```

## standardized

```{r}
savename = "r11_Standardized"
threshold_change = 100.07    # 
threshold_change_res = 1.51  # <- max groupwise collapsed iqr
ith_condition = c("PS.0", "PS.22", "PS.45", "PS.90")
ylab_expression = YLAB_EXPRESSION
width = 10.68
height = 5.81

# overwrite 'gj' with desired parameter
all.data_alias_gj <- all.data
all.data_alias_gj <- all.data_change_gj %>% 
  mutate(gj = r11)  # <------------------------------------------------------ !!!

# Boilerplate ------------------------------------------------------------------
temp_2 <- mk_annotated_delta_df(
  all.data = all.data_alias_gj,
  threshold_change = threshold_change,     # 
  threshold_change_res = threshold_change_res, # <- max groupwise collapsed iqr
  ith_condition = ith_condition
)

# for selecting a reasonable cutoff for threshold change residual
get_grouped_iqrs(df = temp_2)

largest_timewise_iqr <- get_grouped_iqrs_collapse_to_time(df = temp_2)
largest_timewise_iqr
print("-- -- -- -- -- -- -- -- ")
print(as.character(max(largest_timewise_iqr$max_iqr)))
print("-- -- -- -- -- -- -- -- ")


plt1 <- annotated_delta_df_diagnostic(df = temp_2,
                                      threshold_change_res = threshold_change_res)


fm <- mk_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)


fm_reduced <- mk_reduced_asymptotic_model(
  df = temp_2,
  apply_qc = TRUE
)

write_out_fm_res(
  fm = fm, 
  fm_reduced = fm_reduced,
  save_suffix = savename)


predictions <- mk_fm_plotting_df(df = temp_2, fm = fm)


plt2 <- delta_df_prediction_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions)

plt1 + plt2 


plt <- delta_df_publication_plot(
  df = temp_2,
  apply_qc = TRUE,
  predictions = predictions,
  text.size = 20,
  point.size = 2,
  line.size = 3,
  mean.point.size = 2,
  mean.line.size = 2,
  ylab_expression = ylab_expression
  
)


plt


ggsave(here("data", "figures", paste0(savename, ".pdf")), plot = last_plot(), 
       width = width, height = height, units = "in")
ggsave(here("data", "figures", paste0(savename, ".svg")), plot = last_plot(), 
       width = width, height = height, units = "in")
```




## Plotting








# Workspace

```{r}
all.data %>% skimr::skim()
```

```{r}
all.data %>%
  group_by(Condition, Time) %>%
  tally() %>%
  pivot_wider(names_from = Time, values_from = n)
```

```{r}
all.data %>%
  ggplot(aes(x = Time, y = gj, group = Experiment, color = Inj_Cell))+
  geom_line()+
  geom_point()+
  facet_grid(.~Condition)
```

```{r}
#TODO pull out gj as variable
# settings
condition_set <- list(
  c("PS.0.High.Amp",  "PS.22.High.Amp"),
  c("PS.22.High.Amp", "PS.90.HA"),
  c("PS.90.HA.Cd",    "PS.90.HA"),
  c("PS.0", "PS.22", "PS.45", "PS.90"))

# data prep

temp <- all.data %>% dplyr::select(Condition, Experiment, Inj_Cell, Time, gj)

temp.t0 <- temp %>%
  dplyr::filter(Time == 0) %>%
  rename(initial = gj) %>%
  dplyr::select(-Time)

temp <- full_join(temp, temp.t0)
temp$gj = temp$gj - temp$initial

temp$Time <- as.numeric(temp$Time)

# model testing
# can we fit each condition?

all_condition_list = list()
for(ith_condition in unique(temp$Condition)){
  condition_list = list()
  
  print(ith_condition)
  temp_2 <- temp[temp$Condition %in% ith_condition, ]
    
  # does the model fit on all data?
  fm_all_data = try(
                    drm(gj ~ Time, 
                        data = temp_2,
                        fct = AR.2(),
                        pmodels = list(~1,~1))
                    )
  if(typeof(fm_all_data)=="list"){
    res_all_data = summary(fm_all_data)
    res_all_data = res_all_data$coefficients     
    res_all_data = as.data.frame(res_all_data)
    names(res_all_data) <- c("Estimate", "Std..Error", "t-value", "p-value" )
    res_all_data["Experiment"] = "All"
    res_all_data["Inj_Cell"]   = "All"
  } else {
    res_all_data <- data.frame("Estimate"=NA,
                      "Std..Error"=NA,
                      "t-value"=NA,
                      "p-value"=NA ,
                        "Experiment" = "All",
                        "Inj_Cell" ="All")
  }

  # what's the effect of each sub-point?
  obs_df <- temp_2[, c("Experiment", "Inj_Cell")] %>% distinct()
  
  for(jth_obs in seq(1, nrow(obs_df))){
    jth_exp <- obs_df[jth_obs, "Experiment"]
    jth_cell<- obs_df[jth_obs, "Inj_Cell"]
    
    fm_jackknife = ""
    fm_jackknife = try(
                    drm(gj ~ Time, 
                        data = temp_2[, ],
                        fct = AR.2(),
                        pmodels = list(~1,~1))
                    )
    if(typeof(fm_jackknife)=="list"){
      res = summary(fm_jackknife)
      res = res$coefficients     
      res = as.data.frame(res)
      names(res) <- c("Estimate", "Std..Error", "t-value", "p-value" )
      res["Experiment"] = jth_exp
      res["Inj_Cell"]   = jth_cell
      
    } else {
      res <- data.frame("Estimate"=NA,
                        "Std..Error"=NA,
                        "t-value"=NA,
                        "p-value"=NA,
                        "Experiment" = jth_exp,
                        "Inj_Cell" =jth_cell
                        )
    }
    
    condition_list[[length(condition_list)+1]] <- res
    
    
  }
  condition_res <- do.call(rbind, condition_list)
  condition_res <- rbind(res_all_data, condition_res)
  condition_res['Condition'] <- ith_condition
  all_condition_list[[length(all_condition_list)+1]] <- condition_res
    
}
jackknife_results <- do.call(rbind, all_condition_list)
```

```{r}
jackknife_results %>% 
  filter(Estimate < 1000) %>% 
  ggplot(aes(Condition, Estimate, color = Inj_Cell))+
  geom_point()
```

# Test First Comparisons
## PS.0.High.Amp
```{r}
# settings
condition_set <- list(
  c("PS.0.High.Amp",  "PS.22.High.Amp"),
  c("PS.22.High.Amp", "PS.90.HA"),
  c("PS.90.HA.Cd",    "PS.90.HA"),
  c("PS.0", "PS.22", "PS.45", "PS.90"))

ith_condition = "PS.0.High.Amp"

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, 
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~1,~1))

fm_line <- data.frame(Time = seq(0, 80))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  labs(title = ith_condition)
```

## PS.22.High.Amp
```{r}
ith_condition = "PS.22.High.Amp"

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, 
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~1,~1))

fm_line <- data.frame(Time = seq(0, 80))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  labs(title = ith_condition)
```

## Together?

```{r}
threshold_change = 1.4  #1.5 # <- what is the largest change in 20 minutes that we're willing to accept as real?

ith_condition = c("PS.0.High.Amp",  "PS.22.High.Amp")

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]

head(temp_2)

# Get stepwise change
temp_2_diff = temp_2 %>% 
  pivot_wider(names_from =  Time, values_from = gj) %>% 
  mutate(delta00 = 0,
         delta20 = `20`-`0`,
         delta40 = `40`-`20`,
         delta60 = `60`-`40`,
         delta80 = `80`-`60`) %>% 
  pivot_longer(c(delta00, delta20, delta40, delta60, delta80), 
               names_to = "dTime", values_to = "diffgj") %>% 
  dplyr::select(Condition, Experiment, Inj_Cell, dTime, diffgj) %>% 
  mutate(Time = as.numeric(str_remove(dTime, "delta"))) %>% 
  dplyr::select(-dTime)

temp_2 = full_join(temp_2, temp_2_diff)

# we'll look at this to figure out what 
temp_2 %>% 
  ggplot(aes(x = abs(diffgj)))+
  geom_histogram()

# temp_2 <- temp_2 %>%  # <---------------- try changes here
  # filter(gj < 1) %>% 
  # filter(gj > -2.5)

temp_2["absdiffgj"] <- abs(temp_2$diffgj)


temp_2["remove"] = FALSE
temp_2 <- temp_2[!is.na(temp_2$gj), ]
temp_2[temp_2$absdiffgj > threshold_change, "remove"] = TRUE

# flag everything after the first deviation
# assume that if an experiment fails, every time point after it is not to be trusted.
flag_after <- temp_2[temp_2$remove, ]

for(i in seq(1, nrow(flag_after))){
 mask <- (temp_2$Condition == flag_after[i, "Condition" ]) & (
        temp_2$Experiment == flag_after[i, "Experiment" ]) & (
        temp_2$Inj_Cell == flag_after[i, "Inj_Cell" ]) & (
        temp_2$Time >= flag_after[i, "Time"])

  temp_2[mask, "remove"] <- TRUE 
}


# temp_2 <- temp_2[!temp_2$remove, ]
```


```{r}
### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_2[!temp_2$remove,],
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         ~1))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj, color = remove))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'Black', size = 1)+
  # labs(title = ith_condition)+
  facet_grid(.~Condition)
```

```{r}
### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_2[!temp_2$remove,],
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         #~1))
                         ~factor(Condition)))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj, color = remove))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'Black', size = 1)+
  # labs(title = ith_condition)+
  facet_grid(.~Condition)
```

# Test Second Comparisons
## PS.90.HA
```{r}
ith_condition = "PS.90.HA"

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, 
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~1,~1))

fm_line <- data.frame(Time = seq(0, 80))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  labs(title = ith_condition)
```

## PS.90.HA.Cd
```{r}
ith_condition = "PS.90.HA.Cd"

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, 
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~1,~1))

fm_line <- data.frame(Time = seq(0, 80))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  labs(title = ith_condition)
```


## Together?
```{r}
# ith_condition =   c("PS.90.HA.Cd",    "PS.90.HA")
# 
# temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
# ### Does the full set fit?
# fm <- drm(gj ~ Time, Condition,
#           data = temp_2,
#           fct = AR.2(),
#           pmodels = list(~factor(Condition), #~1,
#                          ~1))
# 
# fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
# fm_line["gj"] <- predict(fm, newdata = fm_line)
# ### Does the fit look reasonable?
# temp_2 %>% 
#   ggplot(aes(Time, gj))+
#   geom_hline(yintercept = 0)+
#   geom_point()+
#   geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
#   geom_line(data = fm_line, color = 'red')+
#   # labs(title = ith_condition)+
#   facet_grid(.~Condition)
```

```{r}
# ith_condition =   c("PS.90.HA.Cd",    "PS.90.HA")
# 
# temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
# ### Does the full set fit?
# fm <- drm(gj ~ Time, Condition,
#           data = temp_2,
#           fct = AR.2(),
#           pmodels = list(~factor(Condition), #~1,
#                          #~1))
#                          ~factor(Condition)))
# 
# fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
# fm_line["gj"] <- predict(fm, newdata = fm_line)
# ### Does the fit look reasonable?
# temp_2 %>% 
#   ggplot(aes(Time, gj))+
#   geom_hline(yintercept = 0)+
#   geom_point()+
#   geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
#   geom_line(data = fm_line, color = 'red')+
#   # labs(title = ith_condition)+
#   facet_grid(.~Condition)
```



```{r}
threshold_change = 21.4  #1.5 # <- what is the largest change in 20 minutes that we're willing to accept as real?
threshold_change_res = 1.5

ith_condition = c("PS.90.HA.Cd",    "PS.90.HA")

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]

head(temp_2)

# Get stepwise change
temp_2_diff = temp_2 %>% 
  pivot_wider(names_from =  Time, values_from = gj) %>% 
  mutate(delta00 = 0,
         delta20 = `20`-`0`,
         delta40 = `40`-`20`,
         delta60 = `60`-`40`#,
         # delta80 = `80`-`60`
         ) %>% 
  pivot_longer(c(delta00, delta20, delta40, delta60
                 # , delta80
                 ), 
               names_to = "dTime", values_to = "diffgj") %>% 
  dplyr::select(Condition, Experiment, Inj_Cell, dTime, diffgj) %>% 
  mutate(Time = as.numeric(str_remove(dTime, "delta"))) %>% 
  dplyr::select(-dTime)



temp_2 = full_join(temp_2, temp_2_diff)

# Try adding in residual from groupxtime change
temp_2 <- temp_2 %>%
  ungroup() %>%
  group_by(Condition, Time) %>%
  mutate(median_gj = median(gj)) %>%
  mutate(residual_gj = median_gj - gj) %>%
  ungroup()


# we'll look at this to figure out what 
temp_2 %>% 
  ggplot(aes(x = abs(diffgj)))+
  geom_histogram()

temp_2 %>% 
  ggplot(aes(x = abs(residual_diffgj)))+
  geom_histogram()


temp_2["absdiffgj"] <- abs(temp_2$diffgj)
temp_2["absresidgj"] <- abs(temp_2$residual_gj)


temp_2["remove"] = FALSE
temp_2 <- temp_2[!is.na(temp_2$gj), ]
temp_2[temp_2$absdiffgj > threshold_change, "remove"] = TRUE
# and add in residual
temp_2[temp_2$absresidgj > threshold_change_res, "remove"] = TRUE


temp_2$Condition <- as.character(temp_2$Condition)
# flag everything after the first deviation
# assume that if an experiment fails, every time point after it is not to be trusted.
flag_after <- temp_2[temp_2$remove, ]

for(i in seq(1, nrow(flag_after))){
 mask <- (temp_2$Condition == unlist(flag_after[i, "Condition" ])
     ) & (temp_2$Experiment == unlist(flag_after[i, "Experiment" ])
     ) & (temp_2$Inj_Cell == unlist(flag_after[i, "Inj_Cell" ])
     ) & (temp_2$Time >= unlist(flag_after[i, "Time"]))

  temp_2[mask, "remove"] <- TRUE 
}


# temp_2 <- temp_2[!temp_2$remove, ]
```


```{r}
### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_2[!temp_2$remove,],
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         ~1))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj, color = remove))+
  geom_line(aes(y = median_gj+threshold_change_res), color = "red", size = 1)+
  geom_line(aes(y = median_gj), color = "red", size = 1)+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'Black', size = 1)+
  # labs(title = ith_condition)+
  facet_grid(.~Condition)
```

```{r}
### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_2[!temp_2$remove,],
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         #~1))
                         ~factor(Condition)))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj, color = remove))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'Black', size = 1)+
  # labs(title = ith_condition)+
  facet_grid(.~Condition)
```





# Test Naturalistic
individually all fit on raw
together post filter only works with constrained time constant

## PS.0
```{r}
ith_condition = "PS.0"

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, 
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~1,~1))

fm_line <- data.frame(Time = seq(0, 80))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  labs(title = ith_condition)
```

## PS.22
```{r}
ith_condition = "PS.22"

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, 
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~1,~1))

fm_line <- data.frame(Time = seq(0, 80))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  labs(title = ith_condition)
```

##  PS.45
```{r}
ith_condition = "PS.45"

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, 
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~1,~1))

fm_line <- data.frame(Time = seq(0, 80))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  labs(title = ith_condition)
```

## PS.90
```{r}
ith_condition = "PS.90"

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, 
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~1,~1))

fm_line <- data.frame(Time = seq(0, 80))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  labs(title = ith_condition)
```

## Together?
```{r}
ith_condition = c("PS.0", "PS.22", "PS.45", "PS.90")

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         ~1))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  # labs(title = ith_condition)+
  facet_grid(.~Condition)
```


```{r}
ith_condition = c("PS.0", "PS.22", "PS.45", "PS.90")

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]
### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_2,
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                        #~1))
                         ~factor(Condition)))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red')+
  # labs(title = ith_condition)+
  facet_grid(.~Condition)
```






```{r}
threshold_change = 21.4  #1.5 # <- what is the largest change in 20 minutes that we're willing to accept as real?
threshold_change_res = 1.5

ith_condition = c("PS.0", "PS.22", "PS.45", "PS.90")

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]

head(temp_2)

# Get stepwise change
temp_2_diff = temp_2 %>% 
  pivot_wider(names_from =  Time, values_from = gj) %>% 
  mutate(delta00 = 0,
         delta20 = `20`-`0`,
         delta40 = `40`-`20`,
         delta60 = `60`-`40`,
         delta80 = `80`-`60`
         ) %>% 
  pivot_longer(c(delta00, delta20, delta40, delta60
                 , delta80
                 ), 
               names_to = "dTime", values_to = "diffgj") %>% 
  dplyr::select(Condition, Experiment, Inj_Cell, dTime, diffgj) %>% 
  mutate(Time = as.numeric(str_remove(dTime, "delta"))) %>% 
  dplyr::select(-dTime)



temp_2 = full_join(temp_2, temp_2_diff)

# Try adding in residual from groupxtime change
temp_2 <- temp_2 %>%
  ungroup() %>%
  group_by(Condition, Time) %>%
  mutate(median_gj = median(gj, na.rm = T)) %>%
  mutate(residual_gj = median_gj - gj) %>%
  ungroup()



temp_2["absdiffgj"] <- abs(temp_2$diffgj)
temp_2["absresidgj"] <- abs(temp_2$residual_gj)


temp_2["remove"] = FALSE
temp_2 <- temp_2[!is.na(temp_2$gj), ]
temp_2[temp_2$absdiffgj > threshold_change, "remove"] = TRUE
# and add in residual
temp_2[temp_2$absresidgj > threshold_change_res, "remove"] = TRUE


temp_2$Condition <- as.character(temp_2$Condition)
# flag everything after the first deviation
# assume that if an experiment fails, every time point after it is not to be trusted.
flag_after <- temp_2[temp_2$remove, ]

for(i in seq(1, nrow(flag_after))){
 mask <- (temp_2$Condition == unlist(flag_after[i, "Condition" ])
     ) & (temp_2$Experiment == unlist(flag_after[i, "Experiment" ])
     ) & (temp_2$Inj_Cell == unlist(flag_after[i, "Inj_Cell" ])
     ) & (temp_2$Time >= unlist(flag_after[i, "Time"]))

  temp_2[mask, "remove"] <- TRUE 
}


# temp_2 <- temp_2[!temp_2$remove, ]
```


```{r}
### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_2[!temp_2$remove,],
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         ~1))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj, color = remove))+
  geom_line(aes(y = median_gj+threshold_change_res), color = "red", size = 1)+
  geom_line(aes(y = median_gj), color = "red", size = 1)+
  geom_line(aes(y = median_gj-threshold_change_res), color = "red", size = 1)+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'Black', size = 1)+
  # labs(title = ith_condition)+
  facet_grid(.~Condition)
```

```{r}
### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_2[!temp_2$remove,],
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         #~1))
                         ~factor(Condition)))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_2 %>% 
  ggplot(aes(Time, gj, color = remove))+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'Black', size = 1)+
  # labs(title = ith_condition)+
  facet_grid(.~Condition)
```


# Global application
```{r}
threshold_change = 21.4  #1.5 # <- what is the largest change in 20 minutes that we're willing to accept as real?
threshold_change_res = 1.5

ith_condition = c(
    "PS.0.High.Amp",  "PS.22.High.Amp",
    "PS.90.HA.Cd",    "PS.90.HA",
    "PS.0", "PS.22", "PS.45", "PS.90")

temp_2 <- temp[temp$Condition %in% c(ith_condition), ]

head(temp_2)

# Get stepwise change
temp_2_diff = temp_2 %>% 
  pivot_wider(names_from =  Time, values_from = gj) %>% 
  mutate(delta00 = 0,
         delta20 = `20`-`0`,
         delta40 = `40`-`20`,
         delta60 = `60`-`40`,
         delta80 = `80`-`60`
         ) %>% 
  pivot_longer(c(delta00, delta20, delta40, delta60
                 , delta80
                 ), 
               names_to = "dTime", values_to = "diffgj") %>% 
  dplyr::select(Condition, Experiment, Inj_Cell, dTime, diffgj) %>% 
  mutate(Time = as.numeric(str_remove(dTime, "delta"))) %>% 
  dplyr::select(-dTime)



temp_2 = full_join(temp_2, temp_2_diff)

# Try adding in residual from groupxtime change
temp_2 <- temp_2 %>%
  ungroup() %>%
  group_by(Condition, Time) %>%
  mutate(median_gj = median(gj, na.rm = T)) %>%
  mutate(residual_gj = median_gj - gj) %>%
  ungroup()



temp_2["absdiffgj"] <- abs(temp_2$diffgj)
temp_2["absresidgj"] <- abs(temp_2$residual_gj)


temp_2["remove"] = FALSE
temp_2 <- temp_2[!is.na(temp_2$gj), ]
temp_2[temp_2$absdiffgj > threshold_change, "remove"] = TRUE
# and add in residual
temp_2[temp_2$absresidgj > threshold_change_res, "remove"] = TRUE


temp_2$Condition <- as.character(temp_2$Condition)
# flag everything after the first deviation
# assume that if an experiment fails, every time point after it is not to be trusted.
flag_after <- temp_2[temp_2$remove, ]

for(i in seq(1, nrow(flag_after))){
 mask <- (temp_2$Condition == unlist(flag_after[i, "Condition" ])
     ) & (temp_2$Experiment == unlist(flag_after[i, "Experiment" ])
     ) & (temp_2$Inj_Cell == unlist(flag_after[i, "Inj_Cell" ])
     ) & (temp_2$Time >= unlist(flag_after[i, "Time"]))

  temp_2[mask, "remove"] <- TRUE 
}
```

## first comparison
```{r}
ith_condition = c(
    "PS.0.High.Amp",  "PS.22.High.Amp"#,
    # "PS.90.HA.Cd",    "PS.90.HA",
    # "PS.0", "PS.22", "PS.45", "PS.90"
    )

temp_subset <- temp_2[!temp_2$remove,] %>% 
  filter(Condition %in% ith_condition)

### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_subset,
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         ~1))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_subset %>% 
  ggplot(aes(Time, gj))+
  # geom_line(aes(y = median_gj+threshold_change_res), color = "cornflowerblue", size = 1)+
  # geom_line(aes(y = median_gj), color = "cornflowerblue", size = 1)+
  # geom_line(aes(y = median_gj-threshold_change_res), color = "cornflowerblue", size = 1)+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red', size = 1)+
  facet_grid(.~Condition)


fm_reduced = drm(gj ~ Time, Condition,
              data = temp_subset, fct = AR.2(),
              pmodels = list(~1,~1))
# is using the treatment effect justified?
anova(fm, fm_reduced)
# ED(fm, c(10, 50, 90))
compParm(fm, "d")
```

## secopnd comparison
```{r}
ith_condition = c(
    # "PS.0.High.Amp",  "PS.22.High.Amp"#,
    "PS.90.HA.Cd",    "PS.90.HA"#,
    # "PS.0", "PS.22", "PS.45", "PS.90"
    )

temp_subset <- temp_2[!temp_2$remove,] %>% 
  filter(Condition %in% ith_condition)

### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_subset,
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         ~1))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_subset %>% 
  ggplot(aes(Time, gj))+
  # geom_line(aes(y = median_gj+threshold_change_res), color = "cornflowerblue", size = 1)+
  # geom_line(aes(y = median_gj), color = "cornflowerblue", size = 1)+
  # geom_line(aes(y = median_gj-threshold_change_res), color = "cornflowerblue", size = 1)+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red', size = 1)+
  facet_grid(.~Condition)


fm_reduced = drm(gj ~ Time, Condition,
              data = temp_subset, fct = AR.2(),
              pmodels = list(~1,~1))
# is using the treatment effect justified?
anova(fm, fm_reduced)
# ED(fm, c(10, 50, 90))
compParm(fm, "d")
```


## third comparison
```{r}
ith_condition = c(
    # "PS.0.High.Amp",  "PS.22.High.Amp"#,
    # "PS.90.HA.Cd",    "PS.90.HA",
    "PS.0", "PS.22", "PS.45", "PS.90"
    )

temp_subset <- temp_2[!temp_2$remove,] %>% 
  filter(Condition %in% ith_condition)

### Does the full set fit?
fm <- drm(gj ~ Time, Condition,
          data = temp_subset,
          fct = AR.2(),
          pmodels = list(~factor(Condition), #~1,
                         ~1))

fm_line <- data.frame(expand.grid(Time = seq(0, 80), Condition = ith_condition))
fm_line["gj"] <- predict(fm, newdata = fm_line)
### Does the fit look reasonable?
temp_subset %>% 
  ggplot(aes(Time, gj))+
  # geom_line(aes(y = median_gj+threshold_change_res), color = "cornflowerblue", size = 1)+
  # geom_line(aes(y = median_gj), color = "cornflowerblue", size = 1)+
  # geom_line(aes(y = median_gj-threshold_change_res), color = "cornflowerblue", size = 1)+
  geom_hline(yintercept = 0)+
  geom_point()+
  geom_line(aes(group = interaction(Experiment, Inj_Cell)))+
  geom_line(data = fm_line, color = 'red', size = 1)+
  facet_grid(.~Condition)


fm_reduced = drm(gj ~ Time, Condition,
              data = temp_subset, fct = AR.2(),
              pmodels = list(~1,~1))
# is using the treatment effect justified?
anova(fm, fm_reduced)
# ED(fm, c(10, 50, 90))
compParm(fm, "d")
```


## end


```{r}
# ii <- 1
# 
# 
# fm_full = drm(gj ~ Time, Condition, 
#               data = ,
#   fct = AR.2(),
#          pmodels = list(
#            # ~1,
#            ~factor(Condition),
#            # ~1
#            ~factor(Condition)
#            ))
# 
# summary(fm_full)
# 
# 
# fm_reduced = drm(gj ~ Time, Condition, 
#               data = temp[temp$Condition %in% condition_set[[ii]], ],
#   fct = AR.2(),
#          pmodels = list(
#            ~1,
#            ~1
#            ))
# 
# # is using the treatment effect justified?
# anova(fm_full, fm_reduced)
# 
# # ED(fm, c(10, 50, 90))
# compParm(fm_full, "d")
# 
# 
# 
# 
# predictions = data.frame(expand.grid(Condition = condition_set[[ii]],
#                                      Time = seq(0, 60)))
# predictions = cbind(predictions,
#                     predict(fm_full, newdata = predictions, se.fit = TRUE)
#                     ) %>%
#   rename(gj = Prediction)

```











Workflow for the effects of each observation set on each parameter
```{r}
## fcns ====
# output: fm, summary of fm, predictions
fit_one_model <- function(indf = temp[mask, ]){
  fm_temp = drm(gj ~ Time,
               data = indf,
               fct = AR.2(),
               pmodels = list(~1,~1))

  res_temp = summary(fm_temp)

  predictions = data.frame(Time = seq(0, 60) )
  predictions = cbind(predictions,
                      predict(fm_temp, newdata = predictions, se.fit = TRUE)
                      ) %>%
    rename(gj = Prediction)

  return(list(fm_temp, res_temp, predictions))
}


# workflow for one:
temp <- all.data[all.data$Condition %in% c(
  # "PS.90.HA.Cd"
  # "PS.90.HA"
  "PS.0.High.Amp"
  # "PS.22.High.Amp"
  # "PS.0"
  # "PS.22"
  # , "PS.45", "PS.90"
  ), ] %>%
  dplyr::select(Condition, Experiment, Inj_Cell, Time, gj)

temp.t0 <- temp %>%
  dplyr::filter(Time == 0) %>%
  rename(initial = gj) %>%
  dplyr::select(-Time)

temp <- full_join(temp, temp.t0)
temp$gj = temp$gj - temp$initial

temp$Time <- as.numeric(temp$Time)


## Check for full dataset in group
fm_all <- fit_one_model(temp)
summary(fm_all)


## use ====
sensitivity_df <- temp[, c("Experiment", "Inj_Cell")] %>% distinct()
# list of results from each removal:
out_list <- map(seq(1, nrow(sensitivity_df)), function(i){
  temp_exp = sensitivity_df[i, "Experiment"]
  temp_cell = sensitivity_df[i, "Inj_Cell"]
  mask = !((temp$Experiment == temp_exp) & (temp$Inj_Cell == temp_cell))

  mod_res = try(fit_one_model(indf = temp[mask, ]))
  if(typeof(mod_res) == "list"){
    out = mod_res[[3]]
    out["Experiment"]= temp_exp
    out["Inj_Cell"]= temp_cell
  
    out["d"] <- mod_res[[2]]$coefficients[1, "Estimate"] # d
    out["e"] <- mod_res[[2]]$coefficients[2, "Estimate"] # e
    
  } else if(typeof(mod_res) == "character"){
    out = data.frame(Experiment= temp_exp, 
                     Inj_Cell= temp_cell)
  }
  return(out)
})

out_df <- do.call(rbind, out_list)


## vis effects of each
plt1 = out_df %>%
  ggplot(aes(x = Time, y = gj,
             group = interaction(Experiment, Inj_Cell),
             color = Experiment))+
  geom_hline(yintercept = 0)+
  geom_line()+
  theme(legend.position = 'none')

plt1.left = out_df %>%
  ggplot(aes(x = 0, y = d,
             group = interaction(Experiment, Inj_Cell),
             color = Experiment))+
  geom_hline(yintercept = 0)+
  geom_point()
  # coord_cartesian(ylim = c(0, -0.6))

plt1.down = out_df %>%
  ggplot(aes(x = e, y = 0,
             group = interaction(Experiment, Inj_Cell),
             color = Experiment))+
  geom_point()


(plt1+plt1.left)/plt1.down


```


```{r}

```










Extension to multiple conditions
```{r}
# TODO convergence failed for the groups with expected no change
# Workflow proposal: if fail then rerun with lm; no slope, no t=0
  # TODO before implementing, rerun falling conditions to see if individual obs are to blame.

# just wrap the above with map
use.conditions <- c(
  "PS.0.High.Amp"
  #   Error in optim(startVec, opfct, hessian = TRUE, method = optMethod, control = list(maxit = maxIt,  : 
#   non-finite finite-difference value [2]
# In addition: Warning messages:
# 1: In sqrt(diag(varMat)) : NaNs produced
# 2: In sqrt(diag(varMat)) : NaNs produced
# 3: In sqrt(diag(varMat)) : NaNs produced
# 4: In sqrt(diag(varMat)) : NaNs produced
# 5: In sqrt(diag(varMat)) : NaNs produced
# 6: In sqrt(diag(varMat)) : NaNs produced
#  Error in drmOpt(opfct, opdfct1, startVecSc, optMethod, constrained, warnVal,  : 
#   Convergence failed 
  
  # "PS.22.High.Amp"
  
  # "PS.90.HA.Cd",
     #  Error in optim(startVec, opfct, hessian = TRUE, method = optMethod, control = list(maxit = maxIt,  : 
     #  non-finite finite-difference value [2]
     # Error in drmOpt(opfct, opdfct1, startVecSc, optMethod, constrained, warnVal,  : 
     #  Convergence failed 
 
  # "PS.90.HA"

  # "PS.0",
  # "PS.22",
  # "PS.45", 
  # "PS.90"
  )
data_pts = all.data[all.data$Condition %in% use.conditions, ]
data_pts.t0 <- data_pts %>%
    dplyr::filter(Time == 0) %>%
    rename(t0 = gj) %>%
    dplyr::select(Condition, Experiment, Inj_Cell, t0)
  
data_pts <- full_join(data_pts, data_pts.t0)
data_pts$gj = data_pts$gj - data_pts$t0
data_pts$Time <- as.numeric(data_pts$Time)

out_all_conditions <- map(use.conditions, function(Condition_i){
  
  # workflow for one:
  temp <- all.data[all.data$Condition %in% c(Condition_i), ] %>%
    dplyr::select(Condition, Experiment, Inj_Cell, Time, gj)
  
  temp.t0 <- temp %>%
    dplyr::filter(Time == 0) %>%
    rename(initial = gj) %>%
    dplyr::select(-Time)
  
  temp <- full_join(temp, temp.t0)
  temp$gj = temp$gj - temp$initial
  
  temp$Time <- as.numeric(temp$Time)
  
  ## use ====
  sensitivity_df <- temp[, c("Experiment", "Inj_Cell")] %>% distinct()
  # list of results from each removal:
  out_list <- map(seq(1, nrow(sensitivity_df)), function(i){
    temp_exp = sensitivity_df[i, "Experiment"]
    temp_cell = sensitivity_df[i, "Inj_Cell"]
    mask = !((temp$Experiment == temp_exp) & (temp$Inj_Cell == temp_cell))
    mod_res = fit_one_model(indf = temp[mask, ])
    
    
    mod_res = try(fit_one_model(indf = temp[mask, ]))
    if(typeof(mod_res) == "list"){
      out = mod_res[[3]]
      out["Experiment"]= temp_exp
      out["Inj_Cell"]= temp_cell
    
      out["d"] <- mod_res[[2]]$coefficients[1, "Estimate"] # d
      out["e"] <- mod_res[[2]]$coefficients[2, "Estimate"] # e
      out["fit"] <- FALSE
      
    } else if(typeof(mod_res) == "character"){
      out = data.frame(
        Time=NA,
        gj=NA,
        SE=NA,
        Experiment= temp_exp, 
        Inj_Cell= temp_cell,
        d=NA,
        e=NA,
        fit = FALSE)
    }
    return(out)
    
    
    # out = mod_res[[3]]
    # 
    # out["Experiment"]= temp_exp
    # out["Inj_Cell"]= temp_cell
    # 
    # out["d"] <- mod_res[[2]]$coefficients[1, "Estimate"] # d
    # out["e"] <- mod_res[[2]]$coefficients[2, "Estimate"] # e
    # 
    # return(out)
  })
  
  out_df <- do.call(rbind, out_list)
  out_df["Condition"] <- Condition_i
  return(out_df)
})

out_all_df <- do.call(rbind, out_all_conditions)

## vis effects of each
plt1 = out_all_df %>%
  ggplot(aes(x = Time, y = gj,
             group = interaction(Experiment, Inj_Cell),
             color = Condition))+
  geom_hline(yintercept = 0)+
  geom_point(data = data_pts)+
  geom_line(data = data_pts)+
  geom_line()+
  theme(legend.position = 'none')+
  facet_grid(.~Condition)

plt1
```
















```{r}
ggplot(temp, aes(Time, gj, #color = Condition,
                 color = Experiment,
                 group = interaction(Experiment, Inj_Cell)))+
  geom_point()+
  geom_line()+
  facet_grid(.~Condition)






fm = drm(gj ~ Time,
         data = temp,
         fct = AR.2(),
         pmodels = list(~1,~1))

res = summary(fm)

res$coefficients[2, "Estimate"] # e




# TODO need a way to handel non-fitting




# d_all is with all the data
# d_less is less a single point
i = 1
for(i in seq(1, nrow(sensitivity_df))){
  print(i)
  fm_temp = NA
  res_temp = NA

  mask = !((temp$Experiment == sensitivity_df[i, "Experiment"]) & (temp$Inj_Cell == sensitivity_df[i, "Inj_Cell"]))
  fm_temp = drm(gj ~ Time,
           data = temp[mask, ],
           fct = AR.2(),
           pmodels = list(~1,~1))
  res_temp = summary(fm_temp)

  sensitivity_df[i, "d_less"] <- res_temp$coefficients[1, "Estimate"] # d
  sensitivity_df[i, "e_less"] <- res_temp$coefficients[2, "Estimate"] # e
}

sensitivity_df


```


```{r}
# adapt within a comparison

## stats ====
fm_full = drm(gj ~ Time, Condition,
         data = indf[
           (mask_0 |
           mask_22 |
           mask_45 |
           mask_90
           ),],
         fct = AR.2(),
         pmodels = list(
           # ~1,
           ~factor(Condition),
           # ~1
           ~factor(Condition)
           ))

summary(fm_full)

fm0 <- drm(gj ~ Time, Condition, data = indf[
           (mask_0 |
           mask_22 |
           mask_45 |
           mask_90
           ), ],
          fct = AR.2(),
    pmodels = list(~1, # d
                   ~1                  # e
                   ))
# is using the treatment effect justified?
anova(fm_full, fm0)

# ED(fm, c(10, 50, 90))
compParm(fm_full, "d")
```



```{r}

temp <- M.clean[M.clean$Condition %in% c(
  # "PS.90.HA.Cd", "PS.90.HA"
  # "PS.0.High.Amp", "PS.22.High.Amp"
  "PS.0", "PS.22", "PS.45", "PS.90"

                                         ), ] %>%
  dplyr::select(Condition, Experiment, Inj_Cell, Time, gj) %>%
  group_by(Condition, Experiment, Inj_Cell, Time) %>%
  summarise(gj = mean(gj, na.rm = T)) %>%
  ungroup() %>%
  # mutate(Time = as.character(Time)) %>%
  pivot_wider(names_from = Time, values_from = gj) %>%
  mutate(`20` = `20` - `0`,
         `40` = `40` - `0`,
         `60` = `60` - `0`) %>%
  mutate(`0` = 0) %>%
  pivot_longer(cols = c(`0`, `20`, `40`, `60`), names_to = "Time", values_to = "gj")

# temp =temp[temp$Condition == 'PS.90', ]
temp$Time <- as.numeric(temp$Time)

ggplot(temp, aes(Time, gj, #color = Condition,
                 color = Experiment,
                 group = interaction(Experiment, Inj_Cell)))+
  geom_point()+
  geom_line()+
  # facet_grid(.~Experiment)
  facet_grid(.~Condition)
```


work through low amp
for(entry in c(
  #"180308",
  # "180309",
  "180309a",
  "180314",
  # "180315", # must be included
  "180705",
  "181001"
               )){
  print(entry)
  fm <- drm(gj ~ Time, Condition, data = temp[temp$Experiment != entry, ],
            fct = AR.2(),
      pmodels = list(~1, # d
                     ~1                  # e
                     ))

  print(summary(fm))

}




What's up with 22?
```{r}

library(drc)

indf = temp[temp$Condition %in% c(
  "PS.0",
  "PS.22",
  "PS.45", "PS.90"
  ) , ]

mask_0 <- (indf$Condition == "PS.0")

# keep only ok
mask_22 <- (
  indf$Experiment %in% c(
    "180308",  # works
    # "180309",  # no info
    # "180309a", # no info
    # "180314",  # nans produced  -- added to all working, t value goes to infinity
    "180315",  # works
    # "180705",  # nans produced -- added to working seems ... okay?
    "181001",  # works
    "none") )
mask_22 <- mask_22 | (
  (indf$Experiment %in% c("180314") ) | #& indf$Time != 20
  (indf$Experiment %in% c("180705"))
)

mask_22 <- mask_22 & !((indf$Experiment == "180308") & (indf$Inj_Cell == "LC5"))
mask_22 <- mask_22 & !((indf$Experiment == "181001"
                        ) & (indf$Inj_Cell == "LC5"
                        ) & (indf$Time == 60
                      ))


    # error causing entries
    # (indf$Experiment %in% c("180314") & indf$Time != 20) |
    # (indf$Experiment %in% c("180705") #& indf$Time != 20

mask_45 <- (indf$Condition == "PS.45")
mask_90 <- (indf$Condition == "PS.90")

# indf_filter = indf[, ]
## global-ish ====
# ok -- 0+90
# not - 0+90+45
# not - 0+90+22
# ok -- 22+90
# ok -- 45+90
fm_g = drm(gj ~ Time, Condition,
         data = indf[
           (mask_0 |
            mask_22 |
           mask_45# |
           # mask_90
           ),
                     ],
         fct = AR.2(),
         pmodels = list(~1, ~1))

summary(fm_g)

pred_g = data.frame(Time = seq(0, 60))
pred_g = cbind(pred_g, predict(fm_g, newdata = pred_g, se.fit = TRUE)) %>%
  rename(gj = Prediction)
## 0 ====
fm_0 = drm(gj ~ Time, Condition,
         data = indf[mask_0, ],
         fct = AR.2(),
         pmodels = list(~1, ~1))
summary(fm_0)
pred_0 = data.frame(Time = seq(0, 60),Condition = c("PS.0"))
pred_0 = cbind(pred_0, predict(fm_0, newdata = pred_0, se.fit = TRUE)) %>%
  rename(gj = Prediction)
## 22 ====
fm_22 = drm(gj ~ Time, Condition,
         data = indf[mask_22, ],
         fct = AR.2(),
         pmodels = list(~1, ~1))
summary(fm_22)
pred_22 = data.frame(Time = seq(0, 60),Condition = c("PS.22"))
pred_22 = cbind(pred_22, predict(fm_22, newdata = pred_22, se.fit = TRUE)) %>%
  rename(gj = Prediction)
## 45 ====
fm_45 = drm(gj ~ Time, Condition,
         data = indf[mask_45, ],
         fct = AR.2(),
         pmodels = list(~1, ~1))
summary(fm_45)
pred_45 = data.frame(Time = seq(0, 60),Condition = c("PS.45"))
pred_45 = cbind(pred_45, predict(fm_45, newdata = pred_45, se.fit = TRUE)) %>%
  rename(gj = Prediction)
## 90 ====
fm_90 = drm(gj ~ Time, Condition,
         data = indf[mask_90, ],
         fct = AR.2(),
         pmodels = list(~1, ~1))
summary(fm_90)
pred_90 = data.frame(Time = seq(0, 60),Condition = c("PS.90"))
pred_90 = cbind(pred_90, predict(fm_90, newdata = pred_90, se.fit = TRUE)) %>%
  rename(gj = Prediction)

## plot ====
ggplot(data = indf, aes(Time, gj #color = Condition,
                 # color = Experiment,
                 ))+
  geom_hline(yintercept = 0)+
  geom_line(color = 'darkgray', aes(group = interaction(Experiment, Inj_Cell)))+
  geom_point(color = 'red')+
  geom_point(data = indf[
           (mask_0 |
           mask_22 |
           mask_45 |
           mask_90),
                     ], color = 'darkgray')+
  geom_line(data = pred_g, aes(y = gj), color = 'black', linetype = 'dashed')+
  geom_line(data = pred_0, aes(y = gj, color=Condition))+
  geom_line(data = pred_22, aes(y = gj, color=Condition))+
  geom_line(data = pred_45, aes(y = gj, color=Condition))+
  geom_line(data = pred_90, aes(y = gj, color=Condition))+
  facet_grid(.~Condition)

## stats ====
fm_full = drm(gj ~ Time, Condition,
         data = indf[
           (mask_0 |
           mask_22 |
           mask_45 |
           mask_90
           ),],
         fct = AR.2(),
         pmodels = list(
           # ~1,
           ~factor(Condition),
           # ~1
           ~factor(Condition)
           ))

summary(fm_full)

fm0 <- drm(gj ~ Time, Condition, data = indf[
           (mask_0 |
           mask_22 |
           mask_45 |
           mask_90
           ), ],
          fct = AR.2(),
    pmodels = list(~1, # d
                   ~1                  # e
                   ))
# is using the treatment effect justified?
anova(fm_full, fm0)

# ED(fm, c(10, 50, 90))
compParm(fm_full, "d")

# modelFit(fm)



## plot with FULL MODEL ====

# predict all with full model
pred_00 = data.frame(expand.grid(Time = seq(0, 60),
                     Condition = c("PS.0",  "PS.22", "PS.45", "PS.90")))
pred_00 = cbind(pred_00, predict(fm_full, newdata = pred_00, se.fit = TRUE)) %>%
  rename(gj = Prediction)


ggplot(data = indf, aes(Time, gj #color = Condition,
                 # color = Experiment,
                 ))+
  geom_hline(yintercept = 0)+
  geom_line(color = 'darkgray', aes(group = interaction(Experiment, Inj_Cell)))+
  geom_point(color = 'red')+
  geom_point(data = indf[
           (mask_0 |
           mask_22 |
           mask_45 |
           mask_90),
                     ], color = 'darkgray')+
  # geom_line(data = pred_g, aes(y = gj), color = 'black', linetype = 'dashed')+
  geom_line(data = pred_00, aes(y = gj, color=Condition))+
  # geom_line(data = pred_22, aes(y = gj, color=Condition))+
  # geom_line(data = pred_45, aes(y = gj, color=Condition))+
  # geom_line(data = pred_90, aes(y = gj, color=Condition))+
  facet_grid(.~Condition)

```

